--- 
title: "BY2011 Methodology"
author: "David Holstius"
date: "`r Sys.Date()`"
output: 
  bookdown::gitbook:
    df_print: paged
documentclass: book
description: "This is a reproduction of the BY2011 Methodology Report."
site: "bookdown::bookdown_site"
biblio-style: apalike
link-citations: yes
---

# Introduction

This is a reproduction of the BY2011 Methodology Report, with several enhancements:

- Charts and tables woven throughout the text.
- Equations (ex: [Wineries/Breweries](#wineries-fermentation-methodology)).
- Linked references to rules & regulations (ex: [Chemical Manufacturing](#chem_fac-other-control)).

It's a work in progress, but very useful. There are stubs for many sections in [Chapter 4](#indcom), [Chapter 6](#petprod), and [Chapter 9](#mobile_combust). However, the other seven chapters have lots of good content!

A forked and modified copy can serve as the initial BY2015 Methodology Report.

More features can of course be added (ex: tables of county fractions) to existing sections (and stubs).

```{r libraries, include = FALSE, message = FALSE, cache = TRUE}
library(inventory)
library(BY2011)
```

```{r options, include = FALSE, message = FALSE, cache = FALSE}
#   html_vignette:
#   df_print: kable
#   toc: true
#   toc_depth: 3

library(knitr)
library(printr)

knitr::opts_chunk$set(
  #dev = "svg",
  cache = TRUE,
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.width = 7,
  out.width = 700,
  fig.height = 4,
  out.height = 800 / (8 / 4),
  dpi = 300)
```
