--- 
title: "BY2011 Methodology"
author: "Bay Area Air Quality Management District"
date: "`r Sys.Date()`"
output: 
  bookdown::gitbook:
    df_print: paged
documentclass: book
description: "Recreation of the BAAQMD BY2011 Methodology PDF."
site: "bookdown::bookdown_site"
biblio-style: apalike
link-citations: yes
---

# Introduction

This is a recreation of the [BY2011 Methodology PDF], with several key enhancements:

- **Charts** to illustrate emissions, control profiles, and growth profiles;
- **Tables** with footnotes, dynamic calculations, and values pulled directly from BY2011 data (examples: [Structural Coatings](#petprod-coat-struct-history), [Waste Burning](#waste_burn-planned_ag-methodology), [Accidental Fires](#misc_other-fires-struct-methodology), and [Animal Waste](#misc_other-animal_waste-livestock-methodology));
- **Equations** with rich formatting (examples: [Sandblasting](#indcom-sandblast-calcs), [Paved Roads](#misc_other-roads-paved-methodology), and [Farming Operations](#cat_749-methodology));
- Linked **references** to rules & regulations (example: [Chemical Manufacturing](#chem_fac-other-control)); and
- A list of [errata](#errata), to serve as:
    - a concrete list of things to be fixed in BY2015; and 
    - a resource for learning QA techniques that lead to the uncovering of errata in the first place.

It's a work in progress, but very useful for understanding the BY2011 inventory. A forked copy can serve as the foundation of the **BY2015** Methodology Report.

Use the left and right arrow keys to page through this document. Or, use the table of contents, at left, to jump to a specific section.

```{r libraries, include=FALSE, message=FALSE, cache=TRUE}
library(inventory)
library(BY2011)
```

```{r options, include=FALSE, message=FALSE, cache=FALSE}
#   html_vignette:
#   df_print: kable
#   toc: true
#   toc_depth: 3

library(knitr)
library(printr)

knitr::opts_chunk$set(
  dev = "svg",
  cache = TRUE,
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.width = 8,
  out.width = 800,
  fig.height = 4,
  out.height = 800 / (8 / 4),
  dpi = 300)
```
