--- 
title: "BY2011 Methodology"
author: "David Holstius"
date: "`r Sys.Date()`"
output: 
  bookdown::gitbook:
    df_print: paged
documentclass: book
description: "This is a reproduction of the BY2011 Methodology Report."
site: "bookdown::bookdown_site"
biblio-style: apalike
link-citations: yes
---

# Introduction

This is an enhanced reproduction of the BY2011 Methodology Report, featuring:

- **Charts** to illustrate historical emissions, control profiles, and growth profiles;

- **Tables** with footnotes, dynamic calculations, and values pulled directly from BY2011 data (examples: [Structural Fires](#misc_other-fires-struct-methodology), [Waste Burning](#waste_burn-planned_ag-methodology), and [Animal Waste](#misc_other-animal_waste-livestock-methodology));

- **Equations** with rich formatting (examples: [Paved Roads](#misc_other-roads-paved-methodology) and [Farming Operations](#cat_749-methodology)); and

- Linked **references** to rules & regulations (example: [Chemical Manufacturing](#chem_fac-other-control)).

It has two main purposes:

- **Understanding.** It's a work in progress, but very useful for understanding the BY2011 inventory. There are stubs for many sections in [Chapter 4](#indcom), [Chapter 6](#petprod), and [Chapter 9](#mobile_combust). However, the other seven chapters have lots of good content.

- **BY2015.** A forked and modified copy can serve as the initial BY2015 Methodology Report.

Potential enhancements include:

- Adding tables or visualizations of county fractions.
- Adding more internal cross-references.
- Finishing hyperlinks to BAAQMD rules & regulations.
- Add hyperlinking to external documents (reports, etc.).
- Creating a Bibliography (bookdown has good support for this).
- Adding an Appendix with supplementary datasets (e.g. CEC natural gas consumption).
- Adding an Appendix showcasing major changes from the previous inventory.

```{r libraries, include = FALSE, message = FALSE, cache = TRUE}
library(inventory)
library(BY2011)
```

```{r options, include = FALSE, message = FALSE, cache = FALSE}
#   html_vignette:
#   df_print: kable
#   toc: true
#   toc_depth: 3

library(knitr)
library(printr)

knitr::opts_chunk$set(
  dev = "svg",
  cache = TRUE,
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.width = 8,
  out.width = 800,
  fig.height = 4,
  out.height = 800 / (8 / 4),
  dpi = 300)
```
