## Incineration

```{r waste-burn-incineration-setup}
THESE_CATEGORIES <- c(
  "#314 Incineration (Point)" = 314,
  "#1579 Incineration (Area)" = 1579)
```

### Emissions

#### Introduction {-}

These categories estimates criteria pollutant (particulate, organic, NO~x~, SO~x~, and CO) and greenhouse gas (GHG) emissions (Biogenic-CO~2~, CH~4~, and N~2~O) from waste material combustion at dwellings (e.g., in fireplaces and apartment house incinerators), commercial firms (e.g., in crematories and pathological incinerators), and industrial plants (e.g., in incinerators for waste disposal, reduction or preparation for recycling operations). Category 314 accounts for emissions from point sources in the Air District and emissions for category 1579 were obtained from area sources.

Carbon Dioxide emissions from this category are considered to be biogenic emissions. Biogenic Carbon Dioxide (Bio-CO~2~) emissions are a subset of total CO~2~ emissions which are emitted from materials that are derived from living cells, excluding fossil fuels, limestone and other materials that have been transformed by geological processes. Bio- CO~2~ originates from carbon that is present in materials such as wood, paper, vegetable oils and food, animal, and yard waste.

These categories do not include emissions from the combustion of any "auxiliary fuel" (e.g. natural gas or fuel oil) used to maintain the elevated temperatures needed to promote combustion of the waste material being incinerated (Emissions from such "auxiliary fuels" are covered in categories #307, #309, #1590 and #1591). These categories also do not include emissions from solid fuel combustion for heating, cooking, or recreational purposes, which is covered in category #289.

#### Methodology {-}

##### Point Sources {-}

The District updates the point source (Category 314) data each year on a source-by- source basis using as input the following:

1. Process material throughputs as reported by the plants.

2. Emissions factors (these may be source specific as reported by the plants or general factors, i.e. from the EPA).

3. Emissions control factors (device-specific or general - these may be supplied by the plants also).

##### Area Sources {-}

Area source emissions for category 1579 were calculated based on an estimated household waste generated in the Bay Area. Most of the household waste in the Bay Area is collected and disposed of at the waste landfills. About a third of a percent of the total waste generated the Bay Area is assumed to be burnt through illegal fires. The throughput (tons/year) was estimated by multiplying the Bay Area population by an average amount of waste production per resident. An average residential daily waste production of 1.6 pounds/person/day was used for the Bay Area. The residential daily waste production data was obtained from the California Integrated Waste Management Board for the year 1998. 

The emission factors for category 1579, in pounds per ton (Lb/Ton) of waste materials combusted are shown below.

```{r waste-burn-incineration-emfac-table}
BY2011_annual_area_source_emission_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_emission_factors(
    pollutants = union(
      BY2011_POLLUTANTS,
      c("CO2_bio")),
    digits = 3,
    caption = "Emission factors (lb/ton).")
```

Emission factors were developed based on type of materials commonly disposed of in this manner. EPA's document AP-42 contains information on combustion of waste materials. The fuel specific emission coefficients for GHGs were obtained from the U.S. Department of Energy’s (DOE’s) Energy Information Administration (EIA), the U.S. Environmental Protection Agency’s (EPA’s) document AP-42, and the California Energy Commission (CEC).

### Trends

#### History {-}

```{r waste-burn-incineration-emission-chart, fig.height=12, out.height=1200}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

Historical emission trends followed area population growth.

#### Growth {-}

```{r waste-burn-incineration-growth-chart, fig.height=4, out.height=400}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

It was assumed that annual emission trends for waste burning would follow population growth in the Bay Area. The population growth data was obtained from the Association of Bay Area Government's (ABAG’s) 2009 "Projections" reports.

#### Control {-}

The District [Regulation 9] controls emissions of NO~x~ and SO~x~ from combustion of solids.

***

By: Sukarn Claire 
Date: January 2014 
Base Year: 2011
