## Contaminated Soil Aeration

```{r indcom-soil-aeration-setup}
THESE_CATEGORIES <- c(
  "#37 Contaminated Soil Aeration" = 37)
```

### Emissions

#### Introduction {-}

Category 37 accounts for organic emissions from contaminated soil aeration events. Contaminated soil aeration occurs when soil containing organic compounds is excavated and allowed to vent into the open air. These events include underground gasoline tank removal, soil excavation during pipeline leak repairs, and removal of other organic and petroleum chemical spills.

#### Methodology {-}

The District requires a written report for any soil aeration activity. These reports were evaluated to determine a generalized emission factor for each event as well as to estimate the total number of excavations.

Regulation 8, Rule 40 allows up to 150 pounds per day of organic compound emissions per aeration event. The organic compound emissions factor was calculated assuming the aeration site starts emitting at 120 pounds per day, with emissions halving every ten days, and with emissions set at zero at the 90th day. Two tank removals or replacements are also assumed to occur per aeration event. On average, about 250 excavation events take place annually in the Bay Area.

#### County Distribution {-}

The county activity distribution is based on an average number of aeration events in each county in the District.

#### Monthly Variation {-}

The monthly factors are assumed to be uniform. More aeration events are assumed to start during weekdays than during weekends.

### Trends

#### History {-}

```{r indcom-soil-aeration-emission-chart}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_annual_emissions_by(
    fill = category)
```

State regulations governing the construction standards of gasoline holding tanks required many stations to replace their existing tanks. In our Source Inventory of 1987, the District had 152 excavation events reported. In 1990, this number had grown to 1254. The number of excavations remained above 1100 per year through the mid 1990s.

#### Growth {-}

```{r indcom-soil-aeration-growth-chart}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr)
```

Much of the increase since 1987 had been due to the Porter and Cologne Act regulated by the State Water Resources Control Board and California Regional Water Quality Control Boards. Parts of these underground tank regulations govern the replacement of underground storage tanks.

The California Code of Regulations, Title 23, Division 3, Chapter 16 stated that by December 22, 1998, all underground storage tanks containing hazardous substances, other than those containing motor vehicle fuels, need to be retrofitted with secondary containment. By the same date, motor vehicle fuel tanks made of steel needed to be retrofitted with secondary containment or be provided with both interior lining and exterior cathodic protection.

The number of excavation events remained at close to the 1990 rate through 1998 and declined afterwards.

#### Control {-}

```{r indcom-soil-aeration-control-chart}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant)
```

The District adopted Regulation 8, Rule 40 on February 15, 1989. The overall control afforded by this rule is 81%. This rule applies for soil aeration events only. Air stripping and soil excavation events are inventoried in category 937, under Regulation 8, Rule 47.

Rule 40 sets the rate of uncontrolled aeration in addition to describing an acceptable soil aeration procedure. For an uncontrolled aeration, an operator may not aerate the soil at above certain rate per day; however, the soil aeration may be extended over many days. This does not reduce the total emissions from an aeration event.

***

By: Sukarn Claire 
Date: January 2014 
Base Year: 2011
