## Other Food & Agricultural Processing

```{r indcom-food_ag-other-setup}
THESE_CATEGORIES <- c(
  "#33 Other Food & Ag Processing" = 33)
```

### Emissions

#### Introduction {-}

The category includes emissions from processing plants of miscellaneous food and agricultural products for human or animal consumption such as: coffee and cocoa bean roasting; grain feed milling/packaging; spice/flavoring handling; sugar refinery; onion, garlic, corn, and pet food processing.

#### Methodology {-}

This category consists only of point sources that are contained in the District Data Bank system. Individual companies report information on plant equipment, operating data, and source throughput. This information is updated upon permit renewal in the District’s Data Bank. Criteria pollutant emissions calculated by using throughput data of the specific materials, emission factors based on various test data and publications, operating times, batch cycle variables, and control equipment reduction factors.

Carbon dioxide (CO~2~) emissions are produced during the fermentation process of beer production and in the combustion of organic emissions from coffee and cocoa beans in abatement devices, such as an afterburner. The CO~2~ emissions emitted from beer production is considered biogenic.

#### Monthly Variation {-}

Monthly distribution was estimated to be the same throughout the year due to the variety of processing facilities.

#### County Distribution {-}

The county location of each company as reported in the Data Bank is used to distribute emissions into each county.

### Trends

#### History {-}

```{r indcom-food_ag-other-emission-chart, fig.height=12, out.height=1200}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category)
```

The historical growth profile was based on a combination of prior emissions data (back to 1987) and the Association of Bay Area Government’s (ABAG’s) 2009 Manufacturing & Wholesale Employment data.

#### Growth {-}

```{r indcom-food_ag-other-growth-chart}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr)
```

Projections of emissions to 2030 were based on ABAG’s 2009 Manufacturing & Wholesale Employment data.

#### Control {-}

Emissions through the years were estimated by using agricultural production data in the District. In 1963-1964 there was at least 50% reduction of particulate emissions from equipment such as coffee roaster and food dryers brought about by the District's Regulation 6 on visible emissions from the Ringlemann 2 standard. In 1970 there was at least an additional 25% reduction in particulates from the Ringlemann 1 standard. Currently, there is an estimated 98% overall control of particulates from this category.

```{r indcom-food_ag-other-control-chart}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant)
```

Emissions through the years were estimated by using agricultural production data in the District. In 1963-1964 there was at least 50% reduction of particulate emissions from equipment such as coffee roaster and food dryers brought about by the District's Regulation 6 on visible emissions from the Ringlemann 2 standard. In 1970 there was at least an additional 25% reduction in particulates from the Ringlemann 1 standard. Currently, there is an estimated 98% overall control of particulates from this category.

***

By: Stuart Schultz 
Date: October 2013 
Base Year 2011
