## Wineries/Breweries - Aging

```{r indcom-winery-aging-setup}
THESE_CATEGORIES <- c(
  "#32 Wineries/Breweries, Aging" = 32)
```

### Emissions

#### Introduction {-}

This category consists of both area and point sources. The area source accounts for the ethanol emissions from aging of brandy. Brandy is produced from a distillation process, separating ethanol and other volatile substances from fermented juices. The brandy is then aged for a period of two to ten years. During the aging process, usually, in 50-gallon oak barrels, there is a considerable amount of ethanol emissions released from the barrels into the atmosphere. The point source portion accounts for organic emissions from brewery sources contained in the District’s Data Bank.

#### Methodology {-}

San Joaquin Valley District estimated 4,561,546 gallons of brandy in 2007. The 57,380 barrels of Brandy in Bay Area were estimated based upon the above reported data.

An emission factor for a 50-gallon Brandy barrel was derived by the Wine Institute. The assumption being: brandy is 120 proof (60% alcohol) on the average; and alcohol is lost during aging at a rate of 2.5% per year per barrel. This resulted in an emission factor of 4.96 lbs. ethanol per barrel of Brandy.

Emissions calculations from the aging of brandy consist of multiplying the emission factor with the amount of brandy barrels in storage in the District. The methodology is presently based on ARB's methodology (Section 5-2).

#### Monthly Variation {-}

Brandy is aged for a period of years, during which emissions are released 365 days per year and 24 hours per day.

#### County Distribution {-}

County distribution is based on the number of 50-gallon brandy barrels in each county. Napa, Santa Clara, Solano, and Sonoma counties are assumed to produce or to store the 50-gallon brandy barrels.

### Trends

#### History {-}

```{r indcom-winery-aging-emission-chart}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category)
```

From 1980 to 1987, estimated emissions were based on the summary report of the number of alcoholic production facilities in California published by U.S. Department of Census. The number of alcoholic production facilities had been reduced in Santa Clara County due to increasing new electronic manufacturers and housing development. However, grape production has increased since 1988; therefore, emissions were estimated to be at constant level during 1988-1990. In 1993, grape crush was down approximately 7 % from the 1992 crush, and 7 % less than the record-large 1982 crush of 3,115,531 tons. Emissions from 1993 to 1998 are assumed to be constant at the 1993 production level.

#### Growth {-}

```{r indcom-winery-aging-growth-crosswalk}
BY2011_growth_profile_crosswalk %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_growth_crosswalk()
```

```{r indcom-winery-aging-growth-chart}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr)
```

Future projection of emissions was based on the food manufacturing industries taken from ABAG’s 2009 Projections report.

***

By: Michael Nguyen 
Date: January, 2014 
Base Year 2011

