## Large and Small Bakeries

### Emissions

#### Introduction {-}

```{r indcom-bakery-setup}
THESE_CATEGORIES <- c(
  "#28 Large Bakeries" = 28,
  "#935 Small Bakeries" = 935)
```

Emissions from these categories are from large commercial bakeries as well as smaller bakeries. Bread is produced either by sponge-dough process, brews (or liquid sponges) process, or straight-dough process. Commercial bakeries more often use the sponge-dough process, where ingredients are initially mixed, bread dough fermented from 3 to 5 hours, and then baked in ovens at about 450 °F. Bakery products such as sweet rolls, crackers, pretzels, cakes, cookies, doughnuts, biscuits, etc. are either leavened by yeast or by baking powder. Yeast metabolizes the sugars and starches in the dough during fermentation process. The end product of this chemical reaction is primarily carbon dioxide and ethanol (TOG).

The major criteria pollutant emitted from bread baking is primarily ethanol, which is a by-product of the leavening process. Emissions of combustion products from the burning of fuel in the ovens stacks are not considered in this category. Carbon dioxide (CO~2~) is calculated from the combustion of the ethanol from the bread in an abatement device such as an afterburner. The abatement devices are used on the larger (point source) ovens. There is no CO~2~ emission data from the fermentation process available at this time.

### Methodologies

Throughput information from large bakeries are reported and stored in the District's Data Bank system. Source tests, which are conducted at various times, provide the data for criteria pollutant emission factors. (During the rulemaking process in the late 1980’s, fifteen ovens from six large bakeries in the Bay Area were source tested by the District. Ethanol (TOG) emissions ranged from 0.3 to 7.0 pounds per thousand pounds bread produced, depending on the oven size, operating temperature, and type of product.) As mentioned above, CO~2~ emissions are estimated from the combustion of ethanol from the bread in an abatement device. Emissions from these larger bakeries are called point sources (Category #28).

There are numerous smaller bakeries in the Bay Area, which are not in the Data Bank system. These bakeries use smaller ovens. Source test results showed an emission factor of 5.4 pounds ethanol per ton of bread produced. Emissions from these smaller bakeries are called area sources (Category #935).
Throughput data for small bakeries was based on a survey regarding the large bakeries. Small bakeries showed an approximately 37% share of the total bread market. The 2011 average daily throughput from smaller bakeries was calculated to be about 79,676 tons/year. TOG emissions from small bakeries were 1,179 pounds/day (0.59 ton per day)

#### Monthly Variation {-}

For large bakeries, monthly distribution was based on each company's reported quarterly seasonal percent throughput data. For small bakeries (area sources), monthly distribution was based on a 1990 production of a large bakery, which is assumed to be typical.

#### County Distribution {-}

The county locations and associated emissions of each of the large bakeries were used to distribute countywide emissions. For small bakeries, the number of employees in the large bakeries was subtracted from the total number of employees in each county’s bakeries. This data was found in the U.S Census Department’s 2010 County Business Patterns.

```{r indcom-bakery-county-fraction-table}
BY2011_county_fraction_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_county_fractions()
```

### Trends

#### History

```{r indcom-bakery-emission-chart, fig.height=10, out.height=1000}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category)
```

```{r indcom-bakery-BY-vs-DB-chart, fig.height=10, out.height=1000}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY_vs_DB_point_source_annual_emissions()
```

Historical emissions were estimated using actual throughputs and the Association of Bay Area Government’s (ABAG’s) 2009 Manufacturing and Wholesale Employment growth profile. District [Regulation 8, Rule 42](https://www.baaqmd.gov/rules-and-compliance/rules/reg-8-rule-42-large-commercial-bread-bakeries) set standards for new and modified bakery ovens on large commercial bakeries effective January of 1989.

#### Growth {-}

```{r indcom-bakery-growth-crosswalk}
BY2011_growth_profile_crosswalk %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_growth_crosswalk()
```

```{r indcom-bakery-growth-chart}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr)
```

Emissions projections to 2030 were also based on ABAG’s 2009 Manufacturing and Wholesale Employment growth profile.

#### Control {-}

```{r indcom-bakery-control-chart, fig.height=3, out.height=300}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant)
```

District [Regulation 8-42] was amended requiring control equipment for existing ovens, which commenced operation prior to January 1989. This became effective beginning January 1992. Currently, there is an estimated 82% overall control (for large bakeries) on TOG emissions because of this rule.

***

By: Stuart Schultz 
Date: October 2013 
Base Year 2011
