## Fiberglass Manufacturing

```{r indcom-mfg-fiberglass-setup}
THESE_CATEGORIES <- c(
  "#45 Fiberglass Manufacturing" = 45)
```

### Emissions

#### Introduction {-}

Emissions from this category are from fiberglass products manufacturing plants. Organic compounds are used for the production or rework of product by mixing, pouring, hand laying-up, impregnating, injecting, forming, spraying, and/or curing unsaturated polyester materials with fiberglass, fillers or any other reinforcement materials and associated clean- up. The evaporation of these organic compounds, are considered as emissions from this category.

#### Methodology {-}

This category contains emissions from point sources only. Information on equipment, operating data, and throughput of each source are reported by individual manufacturing plants and are stored in the District's Data Bank. Emissions are calculated by using the throughput data of specific materials reported and emission factors that are based on various test data and publication. This information is updated upon permit renewal.

#### Monthly Variation {-}

Monthly distribution was estimated based on each company's reported quarterly seasonal percent throughput data.

#### County Distribution {-}

The county location of each company as reported in the Data Bank is used to distribute emissions into each county.

```{r indcom-mfg-fiberglass-county-fraction-table}
BY2011_county_fraction_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_county_fractions()
```

### Trends

#### History {-}

```{r indcom-mfg-fiberglass-emission-chart}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

The historical growth profile was based on a combination of prior emissions data (back to 1990) and the Association of Bay Area Government’s (ABAG’s) 2009 Manufacturing Employment growth profile.

#### Growth {-}

```{r indcom-mfg-fiberglass-growth-crosswalk}
BY2011_growth_profile_crosswalk %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_growth_crosswalk()
```

```{r indcom-mfg-fiberglass-growth-chart, fig.height=3, out.height=300}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr)
```

Projections to year 2030 were also based on the ABAG’s 2009 Manufacturing Employment growth profile.

#### Control {-}

```{r indcom-mfg-fiberglass-control-chart, fig.height=3, out.height=300}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant)
```

District Regulation 8, Rule 50 effective June 1991 has set standards requirements in polyester resin operations. Currently, it is estimated the overall control of this rule is approximately 87%.

***

By: Stuart Schultz 
Date: November 2013 
Base Year 2011
