## Air Stripping and Soil Vapor Extraction

```{r indcom-soil-extraction-setup}
THESE_CATEGORIES <- c(
  "#937 Soil Vapor Extraction" = 937)
```

### Emissions

#### Introduction {-}

This category accounts for the emissions from air stripping and soil vapor extraction processes. Soil and groundwater contamination are the result of leaking underground storage tanks, accidental spills and landfill leachate. Air stripping process is commonly used for contaminated groundwater remediation. Contaminated groundwater is pumped into the air-stripping tower. A blower generally exhausts the effluent air stream from the stripping column. The contaminated air stream is routed to an air pollution control device (i.e., carbon adsorbers). Soil vapor extraction is one of the techniques to extract volatile organic compounds (VOC) from contaminated soil through the use of a vacuum system. Fresh air is injected into the subsurface at locations around the contaminated area. The contaminated air is withdrawn under vacuum from extraction wells. This contaminated air is then vented directly to a VOC treatment system such as carbon adsorbers, thermal incinerators, catalytic incinerators, and condensers prior to being released to the atmosphere.

#### Methodology {-}

This category contains emissions from point sources only. Point source emissions are calculated from each equipment’s operating data submitted as part of the permit approval process. The Data Bank contains throughput information submitted by individual plants by sources. Emissions are then calculated by using specific emission factors for a particular source operation supplied by the company. If no specific factor is available, a generalized factor developed by district staff engineer is used to determine emissions.

#### Monthly Variation {-}

The data bank contains percentage of throughput data for each of the four 3-month seasonal periods: (December - February, March - May, June - August, September - November).

#### County Distribution {-}

The data bank system contains information on the county location of each processing plant; hence, emissions are distributed to the counties accordingly.

### Trends

#### History {-}

```{r indcom-soil-extraction-emission-chart, fig.height=8, out.height=800}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category)
```

The historical growth profile was based on a combination of prior emissions data (back to 1996) and the Association of Bay Area Government’s (ABAG’s) 2009 Manufacturing Employment growth profile.

#### Growth {-}

```{r indcom-soil-extraction-growth-chart}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr)
```

Future projections of emissions to 2030 are based on ABAG’s 2009 Manufacturing Employment growth profile.

#### Control {-}

```{r indcom-soil-extraction-control-chart}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant)
```

The District adopted Regulation 8, Rule 47 on December 20, 1989. This rule requires all facilities to control emissions by at least 90%; however, based on emissions data, the overall control efficiency is estimated at 96%.

***

By: Stuart Schultz 
Date: November 2013 
Base Year 2011
