## Glass and Related Products

```{r indcom-mfg-glass-setup}
THESE_CATEGORIES <- c(
  "#40 Glass and Related Products" = 40)
```

### Emissions 

#### Introduction {-}

The main pollutant emitted by glass manufacturing plant is particulates in the form of dust. Particulates result from volatilization of materials in the melt that combine with gases and form condensates. Emissions from the forming and finishing phase depend upon the type of glass being manufactured. Emissions for glass and related product manufacturing can be categorized by three production phases: raw materials handling, glass melting and refining, and forming and finishing. The raw materials handling phase is the major fugitive dust emissions. The emissions are generated at each of the material transfer points. The emissions from forming and finishing phase are solid particles of glass and related products. (Nitrogen Oxide, NO~x~, emissions are the result of electric furnace operation; sulfur dioxide, SO~2~, emissions are the result of glass melting in furnaces.)

#### Methodology {-}

Emissions for this category were obtained from point source data only. The Data Bank contains throughput information submitted by the plants by sources. Emissions are then calculated by using specific emission factors for a particular source operation supplied by the company. The summation of these emissions provides the emissions for the category. Emissions from storage of organic liquids or combustion of fuels at glass and related product manufacturing facilities are accounted for in other categories.

#### Monthly Variation {-}

The data bank contains percentage of throughput data for each of the four 3-month seasonal periods: (December - February, March - May, June - August, September - November).

#### County Distribution {-}

The data bank system contains information on the county location of each processing plant; hence, emissions are distributed to the counties accordingly.

```{r indcom-mfg-glass-county-fraction-table}
BY2011_county_fraction_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_county_fractions()
```

### Trends

#### History {-}

```{r indcom-mfg-glass-emission-chart, fig.height=12, out.height=1200}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

```{r indcom-mfg-glass-BY-vs-DB-chart, fig.height=16, out.height=1600}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY_vs_DB_point_source_annual_emissions()
```

The historical growth profile was based on a combination of prior emissions data (back to 1987) and the Association of Bay Area Government's (ABAG's) 2009 Manufacturing Employment growth profile.

#### Growth {-}

```{r indcom-mfg-glass-growth-crosswalk}
BY2011_growth_profile_crosswalk %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_growth_crosswalk()
```

```{r indcom-mfg-glass-growth-chart, fig.height=3, out.height=300}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr)
```

Projections of emissions to 2030 were based on ABAG's 2009 Manufacturing Employment growth profile.

#### Control {-}

```{r indcom-mfg-glass-control-chart, fig.height=3, out.height=300}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant)
```

In 1963, there was at least 50% reduction of particulate emissions from equipment brought about by the District's [Regulation 6] on visible emissions from the Ringlemann 2 standard. In 1970 there was at least an additional 25% reduction in particulates from the Ringlemann 1 standard. Currently, there is an approximate 74% overall control of particulates from this category.

***

By: Stuart Schultz 
Date: November 2013 
Base Year 2011
