## Rubber Manufacturing

```{r indcom-mfg-rubber-setup}
THESE_CATEGORIES <- c(
  "#46 Rubber Products Mfg." = 46,
  "#1910 Rubber Products Mfg. (Area)" = 1910)
```

### Emissions

#### Introduction {-}

Emissions from this category are from rubber fabrication industry, including vulcanizing, where raw rubber is compounded by additives and formed into desired shape and cured at required temperature. In the forming steps, large amounts of organic solvent are often used and therefore included in the emissions in this category.

#### Methodology {-}

Throughput information of each source is reported by individual companies and stored in the District's Data Bank System. These Point Source emissions (Category 46) are calculated by using data from a particular source operation and emission factors based on tests and other data publication. If no specific factor is available, a generalized factor is used developed by district staff engineer. Total rubber products production was estimated based on U. S. Department of Commerce “Current Industrial Report on Rubber Products”. In 2011, it was estimated 16,230 tons were used by area sources (Category 1910) not otherwise reported, or part of the District Data Bank system.

The organics emission factor was estimated based on AP-42, for emulsion styrene- butadiene copolymer production. Emulsion latex polymerization is done in batch process, hence smaller usage than emulsion crumb polymerization. An emission factor of 7.54 lbs./ton was derived.
Calculation: (Area Sources, Category 1910):

$$
16,230\ \frac{\text{ton rubber}}{\text{yr}} \times 7.54\ \frac{\text{lb TOG}}{\text{ton rubber}} \div 2000\ \text{lb/ton} \div 365\ \text{day/yr} = 0.17\ \text{ton/day TOG}
$$

#### Monthly Variation {-}

Monthly distribution was estimated based on cyclic production of rubber products industry, and is reported by each company’s quarterly percent throughput.

#### County Distribution {-}

The number of employees within the Rubber Product Manufacturing sector (SIC No. 3262) taken from the 2007 County Business Patterns was used to distribute emissions into the Bay Area counties.

### Trends {-}

#### History {-}

```{r indcom-mfg-rubber-emission-chart}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

```{r indcom-mfg-rubber-BY-vs-DB-chart, fig.height=8, out.height=800}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY_vs_DB_point_source_annual_emissions()
```

The historical growth profile was based on a combination of prior emissions data (back to 1990) and ARB's Rubber Manufacturing Industry growth profile.

#### Growth {-}

```{r indcom-mfg-rubber-growth-chart}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr)
```

Projections to year 2030 were also based on the Association of Bay Area Government’s 2009 Manufacturing Employment growth profile.

***

By: Stuart Schultz 
Date: January 2014 
Base Year 2011
