## Plastic Products Manufacturing

```{r indcom-mfg-plastic-setup}
THESE_CATEGORIES <- c(
  "#47 Plastic Products Mfg." = 47)
```

### Emissions

#### Introduction {-}

Emissions from this category are from plastics products manufacturing plants. Various products are manufactured from plastics, including usage in protective coatings, molding and casting, laminating, adhesives, treatment of textiles, paper and leather, electrical wire and parts, bottles, and others.

Synthetic resins are the materials from which the synthetic plastics are made. Thermosetting resin is molded under heat and pressure and then cooled. Should it be reheated, it will not soften. The thermoplastic resin is also molded under heat and pressure, but must be chilled in order to harden so that it may retain its molded shape. If reheated, it will soften again, and may be shaped anew. The chief raw materials in producing synthetic resins include urea, formaldehyde, phenol, phthalic anhydride, glycerin, acetone, methanol, phenol, and other compounds. During miscellaneous processes such as molding, extrusion, mixing, reacting, curing, drying, and storage, volatile organics from the raw materials, solvent, or other liquid are emitted and considered in this category.

#### Methodology {-}

This category contains emissions from point sources only. Information on equipment, operating data, and throughput of each source are reported by individual manufacturing plants and are stored in the District's Data Bank. Emissions are calculated by using the throughput data of specific materials reported and emission factors that are based on various test data and publication. This information is updated upon permit renewal.

#### Monthly Variation {-}

Monthly distribution was estimated based on each company's reported quarterly seasonal percent throughput data.

#### County Distribution {-}

The county location of each company as reported in the Data Bank is used to distribute emissions into each county.

```{r indcom-mfg-plastic-county-fraction-table}
BY2011_county_fraction_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_county_fractions()
```

### Trends {-}

#### History {-}

```{r indcom-mfg-plastic-emission-chart, fig.height=8, out.height=800}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

```{r indcom-mfg-plastic-BY-vs-DB-chart, fig.height=12, out.height=1200}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY_vs_DB_point_source_annual_emissions()
```

The historical growth profile was based on a combination of prior emissions data (back to 1987) and the Association of Bay Area Government's (ABAG's) 2009 Manufacturing Employment growth profile.

#### Growth {-}

```{r indcom-mfg-plastic-growth-crosswalk}
BY2011_growth_profile_crosswalk %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_growth_crosswalk()
```

```{r indcom-mfg-plastic-growth-chart, fig.height=3, out.height=300}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr)
```

Projections to year 2030 were based on ABAG's 2009 Manufacturing Employment growth profile.

#### Control {-}

```{r indcom-mfg-plastic-control-chart, fig.height=3, out.height=300}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant)
```

District [Rule 8-52], effective June 1, 2000, has set standards requirements for polystyrene, polypropylene, and polyethylene foam product manufacturing operations. Prior to the passage of this rule, sources were subject to the Miscellaneous Operations rule ([Rule 8-2]). Currently, it is estimated the overall control due to these rules is approximately 76%.

***

By: Stuart Schultz 
Date: November 2013 
Base Year 2011
