## Gas Production Fields {#indcom-extract-gas}

```{r indcom-extract-gas-setup}
THESE_CATEGORIES <- c(
  "#49 Gas Production Fields (Point)" = 49,
  "#1576 Gas Production Fields (Area)" = 1576)
```

### Emissions

#### Introduction {-}

Fugitive emissions at natural gas production fields occur from process equipment whenever components in the liquid or gas stream leak. There are several potential sources of leaks, such as valves, flanges, pumps, compressors, and pressure relief valves (PRVs). These emissions occur randomly and are difficult to predict. During gas production, pollutants of concern are volatile organic compounds (VOCs), methane (CH~4~), hydrogen sulfide (H~2~S) and hazardous air pollutants (HAPs). Categories 48 and 1575 account for point and area source emissions from natural gas production fields in the San Francisco Bay Area, respectively.

#### Methodology {-}

##### Point Sources {-}

Emissions for the point source category (#49) were obtained from point source data only, as contained in the District's data bank. The District updates the data each year on a source-by-source basis using as input:

1. Process material throughputs as reported by the plants
2. Emissions factors (these may be source specific factors reported by the plants through source test results or applicable general factors, i.e. from the U.S. Environmental Protection Agency (EPA))
3. Emissions control factors (device-specific or general - these may be supplied by the plants also)

##### Area Sources {- #indcom-extract-gas-methodology-area}

Gas production activity/throughput information for the area sources (Category 1576) in Bay Area counties was obtained from the California Department of Conservation’s Division of Oil, Gas, and Geothermal Resources (DOGGR) report. Emissions are calculated using composite emission factors. The composite emission factors were developed based on information on various processes in gas production from the U. S. Environmental Protection Agency’s document AP-42. Emission factors in pounds per 1000 cubic feet of gas processed (lb/1000 ft3 or lb/MCF) are shown below.

```{r indcom-extract-gas-field-emfac-table}
BY2011_annual_area_source_emission_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_emission_factors(
    pollutants = BY2011_POLLUTANTS,
    digits = 2,
    caption = "Emission factors (lb/1000 ft3).")
```

#### County Distribution {-}

The county activity is based on amount of gas produced in each Bay Area county in accordance with the California Department of Conservation.

#### Monthly Variation {-}

Monthly and daily factors are assumed to be uniform.

### Trends

#### History {-}

```{r indcom-extract-gas-emission-chart, fig.height=6, out.height=600}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

Emission trends have followed the gas production activity trend. Natural gas production in California has been on the increase in recent years. Past years emissions were determined by using actual gas production rate data for each one of the District’s nine counties taken from the Department of Conservation’s report.

#### Growth {-}

```{r indcom-extract-gas-growth-crosswalk}
BY2011_growth_profile_crosswalk %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_growth_crosswalk()
```

```{r indcom-extract-gas-growth-chart}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

Demand for natural in California and the nation has been growing at approximately 0.8 to 1.2% per year. Gas use is up due to its competitive price and environmental attractiveness. Natural gas production in the Bay Area District is expected to grow approximately 1% per year.

#### Control {-}

```{r indcom-extract-gas-control-chart}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant)
```

The Bay Area Air District adopted Regulation 8, Rule 37 on March 20, 1985 to control the amount of emissions at natural gas and crude oil production facilities. This rule has a control of 80% on reactive organic compounds, with a rule effectiveness of 90% reached by 1989.

***

By: Sukarn Claire 
Date: January 2014 
Base Year: 2011
