## Other Miscellaneous Industrial/Commercial {#indcom-misc}

```{r indcom-misc-setup}
THESE_CATEGORIES <- c(
  "#54 Other Industrial/Commercial" = 54)
```

### Emissions

#### Introduction {-}

This category accounts for process emissions from other miscellaneous industrial and commercial plants (i.e. ceramic processing, mixing, grinding and packaging of mineral base products, gypsum wallboard manufacturing, oyster shell processing machines, metal shops, etc.) not accounted for through other District rules.

#### Methodology {-}

This category consists only of point sources that are contained in the District Data Bank system. Individual companies report information on plant equipment, operating data, and source throughput. This information is updated upon permit renewal in the District’s Data Bank. Criteria pollutant emissions calculated by using throughput data of the specific materials, emission factors, and control equipment reduction factors (if applicable). The emissions factor may specific for a particular source operation supplied by the company. If no specific factor is available, a generalized factor developed by a District staff engineer will be used to determine the emissions.

All seven of the greenhouse gases, namely carbon dioxide (CO~2~), biogenic CO~2~, methane (CH~4~), nitrous oxide (N~2~O), hydrofluorocarbons (HFC’s), perfluorocarbons (PFC’s), and sulfur hexafluoride (SF6), are also calculated for applicable sources.

#### Monthly Variation {-}

The data bank contains throughput data for each of the four 3-month seasonal periods (December - February, March - May, June - August, September - November).

#### County Distribution {-}

The data bank system contains information on the county location of each processing plant; hence, emissions are distributed to the counties accordingly.

### Trends

#### History {- #indcom-misc-history}

```{r indcom-misc-emission-chart, fig.height=16, out.height=1600}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

The historical growth profile was based on a combination of prior emissions data (back to 1987) and the Association of Bay Area Government’s (ABAG’s) 2009 Manufacturing & Wholesale Employment growth profile.

#### Growth {-}

```{r indcom-misc-growth-chart, fig.height=3, out.height=300}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

Future projections of emissions to 2030 are based on ABAG’s 2009 Manufacturing & Wholesale Employment growth profile.

***

By: Stuart Schultz 
Date: January 2014 
Base Year 2011
