## Metallurgical, Foundry & Forging Operations, Fugitive, Metal Recycling & Shredding Operations, Metal Recycling & Shredding Operations, Fugitive {#indcom-metal}

```{r indcom-metal-setup}
THESE_CATEGORIES <- c(
  "#33 Foundry & Forging" = 33,
  "#2221 Foundry & Forging (Fugitive)" = 2221,
  "#2222 Recycling & Shredding" = 2222,
  "#2223 Recycling & Shredding (Fugitive)" = 2223)
```

### Emissions

#### Introduction {-}

Foundries, forging operations, and metal recycling and shredding operations are sources of particulate matter (PM) emissions, some of which may be listed as toxic air contaminants, and total organic compounds (TOG), some of which may also be odorous compounds. Foundries and forges process ferrous (iron based) metals, non-ferrous (i.e. aluminum, copper, magnesium, zinc, brass, and bronze), or a combination of both. Metal recycling and shredding facilities collect, sort, and recycle scrap metal. Scrap Metal includes both ferrous and non-ferrous metals and is often shredded.

Point sources (Categories 34 and 2222) include various process equipment associated with the foundry, forging and metal recycling and shredding operations. These equipment include furnaces (cupola, electric arc, reverberatory, etc.), temporary mold and core making, metal casting, cooling, shakeout, and sand reclamation, shredders, etc. These equipment are subject to District regulations and the permit system. However, there may be some exempt sources for which permits are not required that are also considered point sources. Emissions associated with these two categories are PM and TOG.

In addition to point sources, various other processes and emission sources at these facilities, such as tapping pouring and casting, cooling, shakeout, metal management, sorting separation, open spaces, etc. are the primary sources of fugitive emissions. The fugitive PM emissions from these processes and sources are considered area sources (Categories 2221 and 2223).

#### Methodology {-}

Categories 34 and 2222 contain PM and TOG emissions from point sources only. These point source emissions are calculated from operating data submitted for each equipment as part of the permit approval process. Parameters and variables include throughput, emission factors, operating times, batch cycle variables, and stack parameters. For control equipment, the weight percent reduction factors for each pollutant account for emission reduction. Throughput is updated upon permit renewal. The PM and TOG emissions for the point sources are contained in the permit data bank and the summation of these emissions provide the emissions for these categories.

Categories 2221 and 2223 contain PM emissions from area sources. Fugitive PM emissions from Category 2221 were estimated using a BAAQMD engineering analysis of PM emission at four of the larger foundries and forges within the District The fugitive PM emissions at three of these facilities were estimated to be between 60% - 85% of the total (fugitive and abated) PM emissions. The fugitive PM emission at other facility, though small, was estimated from its recycling activity. The fugitive emissions and throughput from these facilities were used to estimate an emission factor. This emission factor along with reported throughputs from the smaller foundries and forging facilities within the District provided fugitive PM emissions from these sources. In 2011, the fugitive PM emission from Category 2221 was estimated to be 0.61 ton/day.

District staff used an engineering analysis of fugitive PM emissions from a recent CEQA analysis conducted for a new facility in West Sacramento, California to estimate fugitive PM emissions from Bay Area scrap metal recycling facilities (Category 2223). In 2011, the fugitive PM emission from Category 2223 was estimated to be 0.12 ton/day.

#### Monthly Variation {-}

Monthly variation of emissions for these categories is assumed to be uniform (i.e. does not vary) throughout the year.

#### County Distribution {-}

For point and area sources, information on the location of each facility was known and the emissions were distributed to the counties accordingly.

### Trends {#indcom-metal-trend}

#### History {-}

```{r indcom-metal-annual_emissions-chart, fig.height=16, out.height=1600}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category)
```

The historical growth profiles were based on a combination of prior emissions data and the Association of Bay Area Government’s (ABAG’s) 2009 Manufacturing Employment growth profile.

#### Growth {-}

```{r indcom-metal-annual_growth-chart, fig.height=8, out.height=800}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr)
```

Projections of emissions to 2030 were based on ABAG’s 2009 Manufacturing & Wholesale Employment growth profile.

#### Control {-}

```{r indcom-metal-annual_control-chart, fig.height=8, out.height=800}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant)
```

In 1963-1970, the particulate emissions were reduced due to the control imposed by Ringlemann requirements from Regulation 6. Currently, there is an estimated 98.5% overall control of particulates from Category 34 and over 99% for Category 2222.

On May 1, 2013, Regulation 12, Rule 13 (Miscellaneous Standards of Performance, Foundry and Forging Operations) was passed. For Category 34, organics will be reduced by approximately 42%, beginning May 1, 2015. For Category 2221, this rule will reduce fugitive particulate emissions by approximately 10% through an Emission Minimization Plan, beginning May 1, 2015.

On May 1, 2013, Regulation 6, Rule 4 (Metal recycling and Shredding Operations) was passed. For Category 2223, this rule will reduce fugitive particulate emissions by approximately 24% through an Emission Minimization Plan, beginning May 1, 2015.

***

By: Stuart Schultz 
Date: February 2014 
Base Year 2011
