## Asphaltic Concrete Plants

```{r indcom-concrete-asphaltic-setup}
THESE_CATEGORIES <- c(
  "#38 Asphaltic Concrete Plants" = 38)
```

### Emissions 

#### Introduction {-}

Asphaltic concrete paving is a mixture of well graded, high quality aggregate and liquid asphaltic cement which is heated and mixed in measured quantities to produce bituminous pavement material.

#### Methodology {-}

All asphaltic concrete plants operating in the Bay Area are in the District's data bank system and considered point sources. The Data Bank contains throughput information submitted by individual asphaltic concrete plants by sources. Emissions are then calculated by using specific emission factors for a particular source operation supplied by the company. If no specific factor is available, a generalized factor developed by district staff engineer will be used to determine emissions.

#### Monthly Variation {-}

Monthly distribution was estimated to have the highest activity during the months of June through November. Lesser activity occurred during the remainder of the year with the least activity occurring during the months of January through March.

#### County Distribution {-}

The data bank system contains information on the county location of each processing plant; hence, emissions are distributed to the counties accordingly.

### Trends

#### History {-}

```{r indcom-concrete-asphaltic-annual_emissions-chart, fig.height=12, out.height=1200}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

```{r indcom-concrete-asphaltic-BY_vs_DB-emissions_chart, fig.height=12, out.height=1200}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY_vs_DB_point_source_annual_emissions()
```

The historical growth profile was based on a combination of prior emissions data (back to 1987) and the Association of Bay Area Government’s (ABAG’s) 2009 Construction Employment growth profile.

#### Growth {-}

```{r indcom-concrete-asphaltic-annual_growth-chart}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

Projections of emissions to 2030 were based on ABAG’s 2009 Construction Employment growth profile.

#### Control {-}

```{r indcom-concrete-asphaltic-annual_control-chart}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant)
```

In 1961-1962, there was a large reduction of particulate due to the control imposed by the District's Ringlemann 2 requirements. In 1971-1972, there was a further reduction of particulates caused by the District's adoption of the more stringent Ringlemann 1 requirements. Currently, there is an estimated greater than 99% overall control of particulates from this category.

***

By: Stuart Schultz 
Date: November 2013 
Base Year 2011
