## Refinery Process Vessel Depressurization

```{r petref_fac-vessel_depress-setup}
THESE_CATEGORIES <- c(
  "#20 Vessel Depressurization" = 20)
```

### Emissions

#### Introduction {-}

Emissions for this category are generated from depressurization of process vessels at petroleum refineries. Generally a standard procedure requires repeated purging of the process vessel with inert gasses to reduce the concentration of organic vapors to below 300 PPM, before venting a vessel to the atmosphere.

#### Methodology {-}

These emissions are from point sources data reported annually. The District updates the data each year on a source-by-source basis using as input:

1. Process material throughputs as reported annually by the refineries.

2. Emissions factors (these may be source specific factors reported by the companies through source test results or applicable general factors, i.e. from the EPA).

3. Emissions control factors (device-specific or general - these may be supplied by the companies also).

Greenhouse gas emission factors are also provided by the individual refineries and/or taken from EPA. Emissions for greenhouse gases including CO2, CH4, and N2O are reported by the refinery during the District’s annual permit renewal process.

The county, month, and day factors are obtained from the data bank's information on each plant's location, seasonal usage, and days per week of operation.

### Trends

#### History {-}

```{r petref_fac-vessel_depress-annual_emissions-chart, fig.height=3, out.height=300}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  BY2011_chart_annual_emissions_by(
    fill = category)
```

Emissions for category 20 have been relatively insignificant for last few years, at less than 5 pounds per day for the entire region.

#### Growth {-}

```{r petref_fac-vessel_depress-annual_growth-chart, fig.height=3, out.height=300}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  BY2011_chart_annual_growth_by(
    color = cnty_abbr)
```

Projected growth for this category is based on the throughput of marine operations. 

#### Control {-}

```{r petref_fac-vessel_depress-annual_control-chart, fig.height=3, out.height=300}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  BY2011_chart_annual_control_factors_by(
    color = pollutant)
```

The District adopted Regulation 8, Rule 10 on July 20, 1983. Overall control afforded by this rule is estimated to be 95%.

By: Tan Dinh
Date: January 2014 
Base Year: 2011
