## Other Waste Management

```{r waste_mgmt-other-setup}
THESE_CATEGORIES <- c(
  "#53 Waste Mgmt, Other" = 53)
```

### Emissions

#### Introduction {-}

This category accounts for emissions from other industrial and commercial - waste management facilities. Emissions from this category were obtained from point source data only, as contained in the District's Data Bank. Greenhouse gas emissions, namely carbon dioxide (CO~2~) was also calculated for this category.

#### Methodology {-}

This category contains emissions from point sources only. The Data Bank contains throughput information submitted by individual plants by sources. Emissions are then calculated by using specific emission factors and control factors, if any, for a particular source operation supplied by the company.

#### Monthly Variation {-}

The data band contains percentage of throughput data for each of the four 3-month seasonal periods: (December - February, March - May, June - August, September - November).

#### County Distribution {-}

The data bank system contains information on the county location of each processing plant; hence, emissions are distributed to the counties accordingly.

### Trends

#### History {-}

```{r waste_mgmt-other-annual_emissions-chart, fig.height=6, out.height=600}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

The historical growth profile was based on a combination of prior emissions data (back to 2005) and the Association of Bay Area Government’s (ABAG’s) 2009 Manufacturing Employment growth profile.

#### Growth {-}

```{r waste_mgmt-other-annual_growth-chart, fig.height=6, out.height=600}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

Projections to year 2030 were also based on ABAG’s 2009 Manufacturing Employment growth profile.

***

By: Stuart Schultz 
Date: February 2011 
Base Year 2008
