## Refinery Fugitive Emissions

```{r petref-fac-fugitive-setup}
THESE_CATEGORIES <- c(
  "#17 Valves & Flanges" = 17,
  "#18 Pump & Compressor Seals" = 18,
  "#19 Pressure Relief Valves" = 19)
```

### Emissions

#### Introduction {-}

Categories 17, 18, and 19 contain refinery fugitive emissions from sealed equipment. These emissions are treated as point sources and are unique to each refinery. Emissions occur from process equipment whenever components such as valves, flanges, pumps, compressors, and pressure relief valves (PRVs) leak due to seal failure. These emissions generally occur randomly and are difficult to predict occurrences.

Valve and flange leaks account for the bulk of total fugitive emissions while pressure relief valves account for the smallest amount of total fugitive emissions.

#### Methodologies {-}

The petroleum refineries are periodically surveyed for the number of mechanical components utilized in an oil refining process. These components include valves, PRVs, pumps, and compressor seals. Individual types of components are summed up and emissions are calculated based on throughputs and specific emission factors.

Emission information from numerous sources is grouped into the above mentioned categories. EPA's AP-42, Chapter 5 contains description of petroleum refining processes and emission factors. Criteria pollutant, mainly total organic compounds, and greenhouse gas emissions, including carbon dioxide (CO~2~), methane (CH~4~), and nitrous oxide (N~2~O) are produced during refining processes. Since refinery emissions are part of point sources, criteria pollutants as well as greenhouse gas data are obtained from the refinery plant as part of the Bay Area Air District annual permit renewal process.

The county, month, and day factors are obtained from information collected in the District’s data bank. Information such as plant's location, seasonal usage, and days per week of operation are also stored in the data bank.

### Trends

#### History {-}

```{r petref-fac-fugitive-emission-chart, fig.height=4, out.height=400}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category)
```

Historical changes in fugitive emissions in the Bay Area have been due to installation of newer process units that supplement rather than replace old process units.

#### Growth {-}

```{r petref-fac-fugitive-growth-chart, fig.height=6, out.height=600}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr,
    base_year = CY(2011))
```

It is expected that fugitive emissions will not increase significantly in future after new units are built to produce reformulated gasoline.

#### Control {-}

```{r petref-fac-fugitive-control-chart, fig.height=6, out.height=600}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant)
```

The District adopted control regulations in 1980 for valves and flanges, pump and compressor seals and PRVs. This marked the first step in the control of fugitive emissions. Control for valves vary widely, gas PRVs are 95% controlled, while heavy liquid valves have negligible control. Most common and significant emission sources are the light liquid service valves, and they are controlled by 65 to 72%.

In 1997 and 1998, the District combined the three previous regulations 8-18, 8-25, and 8- 28, into a single regulation, Equipment Leaks, # 8-18. Regulation 8-25 was deleted. Regulation 8-28 was changed to focus on episodic emissions from the normal operation of pressure relief valves.

During this change the leak standard for only the pressure relief valves was reduced from 10,000 parts per million (ppm) to 500 ppm of total organic compounds. In addition, applicability of the new [Regulation 8-18] was broadened to include all leaking equipment, not just valves, flanges, and other equipment specifically listed in the earlier regulation. The following table summarizes the limits.

<div class="FIXME">
**FIXME: TABLE OMITTED**
</div>

***

By: Tan Dinh
Date: January 2014
Base Year: 2011
