## Resins

### Emissions

#### Introduction {-}

Emissions reported in this category are from operations performed at resin manufacturing facilities. Resin is a semi-solid, water insoluble organic material with little or no tendency to crystallize under standard temperature and atmospheric conditions. Resins are the basic components of plastics and other surface coating formulations. Equipment used in the operations and manufacturing of resins include resin reactor vessels and thinning/blending tanks. The manufacturing of resins produces mostly organic emissions.

#### Methodology {-}

Organic emissions are calculated based on throughput data, material description (i.e. density, percent VOC in coatings, etc.) as reported by the companies via the Bay Area Air District’s "S" and "G" air permit forms. The District obtain each year, as necessary, updates for the data during the permit renewal process. The data is gathered on a source- by-source basis using the following criteria as input:

1. Process material throughputs as reported annually by the chemical manufacturing companies.

2. Emissions factors (these may be source specific factors reported by the companies through source test results or applicable general factors, i.e. from the EPA).

3. Emissions control factors (device-specific or general - these may be supplied by the companies also).

In addition to criteria pollutants, greenhouse gases are also produced in the manufacturing of resins. The greenhouse gas emission factors are provided by the plants and in some instances where they are not supplied, they are taken from EPA literature/publications.

The monthly distribution is estimated based on data from the company's reported quarterly seasonal percent throughput. The county location of each company as reported in the District’s record keeping system (Data Bank) is used to distribute emissions into each county.

### Trends

#### History {-}

```{r chem_fac-resins-annual_emissions-chart, fig.height=6, out.height=600}
BY2011_annual_emission_data %>%
  filter_categories(
    "#24 Resins Manufacturing" = 24) %>%
  BY2011_chart_annual_emissions_by(
    fill = category)
```

Emissions have increased due to increasing demand from related industries, such as plastics and coating manufacturers. District Regulation 8, Rule 36, limiting emissions from resin manufacturing operations was adopted in June 1984.

#### Growth {-}

```{r chem_fac-resins-annual_growth-chart}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    "#24 Resins Manufacturing" = 24) %>%
  BY2011_chart_annual_growth_by(
    color = cnty_abbr)
```

Projections to year 2030 were based on growth profile of ARB's Chemical Manufacturing which is expected to grow at about 2-3 percent per year for the next few years.

#### Control {-}

```{r chem_fac-resins-annual_control_factor_data}
BY2011_annual_control_factor_data %>%
  filter_categories(
    "#24 Resins Manufacturing" = 24) %>%
  BY2011_chart_annual_control_factors_by(
    color = pollutant)
```

It is estimated that the District achieved a 52% reduction in organic emissions due to the implementation of [Regulation 8, Rule 36](https://www.baaqmd.gov/rules-and-compliance/rules/reg-8-rule-36-resin-manufacturing).

By: Tan Dinh
Date: January 2014
Base Year: 2011
