## Domestic Solid Fuel (Wood)

```{r SS_combust-domestic-wood-setup}
THESE_CATEGORIES <- c(
  "#288 Woodstoves" = 288,
  "#289 Fireplaces" = 289)
```

### Emissions

#### Introduction {-}

This methodology is used to estimate the criteria pollutant emissions from residential wood combustion, namely from fireplace and woodstove. Fireplaces are the most commonly utilized wood burning device in a home. They are used primarily for supplemental heating and for aesthetic appeal. Fireplace combustion is characterized by high air-to-fuel ratios and burn rates. Traditional masonry fireplaces typically contain large open fireboxes without combustion air controls and are not highly efficient heating devices. A net heat loss may occur in a residence if colder, outside air is drawn in to replace the inside air used for combustion and lost through the chimney draft. There are also prefabricated (metal) fireplaces which are slightly higher in energy efficiency than masonry fireplaces. Fireplace inserts that fit into the fireplace can increase the heating efficiency by either radiating the heat into the house or venting heated air into the house by air circulating around the insert with the help of a fan.

Woodstoves are used primarily as domestic space heaters and have enclosed fireboxes and dampers to reduce air-to-fuel ratios and burn rates. Since they are stand-alone heating devices, the greater surface area radiates more heat than a fireplace.

The emissions from residential fireplaces and woodstoves are highly variable, depending on the amount of wood burned and the types of woodstoves and fireplaces being used for burning wood. Many assumptions were made with the realization that any variations in one or more of these variables would substantially change the calculations.

#### Methodologies {-}

The emission estimates for woodstoves and fireplaces were derived from BAAQMD’s wood burning survey performed between winter of 2005 and spring of 2006. This survey was performed by True North Research. Data collected from this survey includes wood burning activities via frequency, fuel type, and quantity for the Bay Area nine counties. A compilation and analysis of this data was performed by Dr. David Fairley, BAAQMD’s statistician, in a report entitled “Revised Estimates of Wood Burning in the San Francisco Bay Area Based on Telephone Survey Data”. Statistical estimation methods were used in this report to derive the annual and seasonal amount of wood burned by county. Throughputs were also derived based on data obtained from the survey. A density of 5 lbs per unit of log was assumed in the calculation. Wood stove and fire place emission factors were based on data obtained from ARB and EIIP volume IV. Composite emission factors were calculated for wood stove criteria pollutants based on an average of conventional and EPA phase II wood stove emission factors. The number of conventional versus EPA phase II wood stoves were derived based on a statistical analysis from the 05-06’ winter survey.

In addition to criteria pollutant emission, greenhouse gases for wood smoke are also reported in the emission inventory. Wood smoke carbon dioxide emissions are considered to be biogenic emissions. Biogenic Carbon Dioxide (Bio-CO~2~) emissions are a subset of total CO~2~ emissions which are emitted from materials that are derived from living cells, excluding fossil fuels, limestone and other materials that have been transformed by geological processes. Bio-CO~2~ originates from carbon that is present in materials such as wood, paper, vegetable oils and food, animal, and yard waste. Wood smoke greenhouse gas emission factors are obtained from the Department of Energy’s (DOE’s), Energy Information Administration (EIA).

#### Monthly Variation {-}

The monthly variation for wood burning in woodstoves and fireplaces was also derived from Bay Area’s 2005-2006 telephone survey on wood burning. Monthly variation was estimated based on sample weights assigned from the data analysis. The estimates were appropriately adjusted for county population.

#### County Distribution {-}

There were wide county differences in the amounts of wood burned. For fireplaces, the more urban counties – Alameda, San Francisco and San Mateo – tend to have lower amounts burned per household than counties in more rural parts such as Sonoma and Napa counties. However, because of the large populations, Alameda, Contra Costa and Santa Clara were estimated to contain the largest quantity of logs burned per area. For wood stoves, Sonoma, Marin and Napa have the largest household number of logs burned per household but, again because of population, the largest number of logs burned in wood stoves per area was found in Contra Costa and Santa Clara counties.

### Trends

#### Historical {-}

```{r SS_combust-domestic-wood-annual_emissions-chart, fig.height=12, out.height=1200}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

#### Growth {-}

```{r SS_combust-domestic-wood-annual_growth-chart, fig.height=8, out.height=800}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

Future projections of emissions are based on household growth in the Bay Area from 2009 “Projections” report published by ABAG.

#### Control {-}

```{r SS_combust-domestic-wood-annual_control-chart, fig.height=6, out.height=600}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant) 
```

Control of residential wood combustion currently falls under EPA’s Standards of Performance for New Stationary Sources (NSPS) for residential wood heater (stoves). (This is adopted by reference in the District Regulation 10.) The NSPS required that new residential heaters manufactured on or after July 1, 1988, or sold on or after July 1, 1990 be certified to meet particulate emission standards of 5.5 grams per hour for catalytic wood heaters and 8.8 grams per hour for non-catalytic wood heaters. These are known as Phase I stoves. More restrictive particulate emission standards were set for stoves manufactured on or after July 1, 1990 or sold after July 1, 1992. For catalytic wood heaters this was 4.1 grams per hour and for non-catalytic wood heater this was 7.5 grams per hour. These are known as Phase II stoves. Although EPA has only set emission limits for particulate matter, emission of reactive organic compounds and carbon monoxide are expected to be limited as well.

Natural gas fireplaces, pellet fueled wood stoves, and EPA-certified woodstoves and fireplaces are increasing in popularity every year. Particulate emissions from these heating devices are insignificant. Some cities and counties in the Bay Area have (or are looking at) enacting new ordinances restricting new wood stove and fireplaces to these low particulate emitting heating devices.

In July 2008, the District enacted a rule (Regulation 6, Rule 3) to control emissions from wood-burning devices. This rule limits emissions of particulate matter (PM) and visible emissions (VE) from wood-burning devices, including any wood-burning device, pellet- fueled wood heater or any indoor permanently-installed device burning any solid fuel for aesthetic or space-heating purposes which includes fireplaces. The rule will help to reduce PM emissions from the burning of wood in woodstoves and fireplaces.

***

By: Tan Dinh
Date: January 2014
Base Year: 2011
