## Power Plants: Gas/Oil Turbines

```{r SS_combust-power_plant-turbines_and_distrib-setup}
THESE_CATEGORIES <- c(
  "#297 Oil Fired Turbines" = 297,
  "#1595 Gas Fired Turbines" = 1595,
  "#1596 Transmission/Distribution" = 1596,
  "#1597 Power Imports" = 1597)
```

### Emissions

#### Introduction {-}

Categories 297 and 1595 account for criteria pollutant (particulate, organic, NOx, SOx, and CO) and greenhouse gas emissions (CO2, CH4, and N2O) from oil and gas fired turbines at the electric power plants in the San Francisco Bay Area.

Modern, highly efficient power plants use the gas turbine Combined Cycle (CC). A combined-cycle gas turbine power plant consists of one or more gas turbines equipped with heat recovery steam generators to capture heat from the gas turbine exhaust. Steam produced in the heat recovery steam generators powers a steam turbine generator to produce additional electric power. Use of the otherwise wasted heat in the turbine exhaust gas results in high thermal efficiency compared to other combustion based technologies. Combined-cycle plants currently entering service can convert about 50 percent of the chemical energy of natural gas into electricity. Additional efficiency can be gained in combined heat and power (CHP) applications (cogeneration), by bleeding steam from the steam generator, steam turbine or turbine exhaust to serve direct thermal loads, such as food and chemical processing.

Category 1596 contains estimates of fugitive emissions of Sulfur Hexafluoride (SF6) from power transmission and distribution system in the Bay Area. SF6 is an inorganic very potent greenhouse gas. SF6 is used in the electrical industry as a gaseous dielectric medium for high-voltage circuit breakers, switchgear, and other electrical equipment. SF6 gas has a much higher dielectric strength than air or dry nitrogen that makes it possible to significantly reduce the size of electrical gear.

Indirect greenhouse gas emission estimates from electricity imports to the Bay Area are accounted for in Category 1597.
Emissions from gas and oil fired steam turbine/boiler type electric power plants are covered in Categories 293 and 294.

#### Methodology {-}

Emissions for Categories 297 and 1595 were obtained from point source data only, as found in the Air District's data bank.

The District updates the data each year on a source-by-source basis using as input:

1. Process material throughputs as reported by the power plants (this data is routinely updated)

2. Emissions factors (these may be source specific as reported by the facility or general factors, i.e. from the Environmental Protection Agency (EPA)

3. Emission control factors (device-specific or general - these may be supplied by the power plants also)

Emissions originate from turbines at various power plants and other facilities in the Bay Area. Many of these turbines are of the "dual fuel" type, i.e., they are able to combust either natural gas or fuel oil. Specific information on these sources allowed them to be identified as either gas or oil fired sources. The EPA's document AP-42 contains this information on dual fuel combustion turbines and engines.

The fuel specific greenhouse gas (GHG) emission coefficients for these categories were obtained from the U.S. Department of Energy’s (DOE’s) Energy Information Administration (EIA), the U.S. Environmental Protection Agency’s (EPA’s) document AP-42, and the California Energy Commission (CEC).

The SF6 emissions for Category 1596 were based on PG&E’s Service Area total fugitive SF6 emissions. The SF6 emissions were apportioned to the Bay Area based on the Bay Area population as compared to total PG&E Service Area population.
Indirect GHG emissions from electricity imported to the Bay Area (Category 1597) were estimated based on total power consumption to power generated locally in the Bay Area. It is estimated that about one fourth to one third of electricity used in the Bay Area is imported from sources outside of the Bay Area. The emission factors (lb. /MWh) used in estimating emissions were in accordance with the PG&E data.

#### County Distribution {-}

The District point source database contains county distribution information for each facility for Category 297 and 1595. County distribution for Category 1596 and 1597 is based on population and power consumption, respectively.

#### Monthly Variation {-}

Monthly variation of emissions is based on company reported quarterly throughput data for C297 and C1595. Uniform activity is assumed for C1596 and C1597.

### Trends

#### History {-}

```{r SS_combust-power_plant-turbines_and_distrib-annual_emissions-chart, fig.height=8, out.height=800}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

Category 297 emissions prior to 1987 were derived from Base Year 1983 trend values. Historical emissions have varied with fuel usage activity. Emission projections for base years prior to 1996 were developed from natural gas and fuel oil usage estimates provided to the District by PG&E.

#### Growth {-}

```{r SS_combust-power_plant-turbines_and_distrib-annual_growth-chart, fig.height=8, out.height=800}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

Category 297 emissions projections for this base year were developed based on the electric power generation forecast by the California Energy Commission (CEC). In the long term, fuel oil usage is projected to be small.

Category 1595 emission projections were developed based on the electric power generation fuel usage forecast by the California Energy Commission (CEC).

Category 1596 emissions are not expected to grow so much as utilities have enrolled in voluntary SF6 emission reduction programs.

Category 1597 emissions are expected to grow in accordance with CEC’s power consumption projections.

#### Control {-}

```{r SS_combust-power_plant-turbines_and_distrib-annual_control-chart}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant) 
```

The Bay Area Air District Regulation 9, Rule 9 controls NOx and CO emissions from fuel combustion in gas turbines.

***

By: Sukarn Claire 
Date: January 2014 
Base Year: 2011
