## Ozone Depleting Substance (ODS) Substitutes

```{r misc_other-ODSS-setup}
THESE_CATEGORIES <- c(
  "#1751 CF4" = 1751,
  "#1752 HFC-125" = 1752,
  "#1753 HFC-134a" = 1753,
  "#1754 HFC-143a" = 1754,
  "#1755 HFC-23" = 1755,
  "#1756 HFC-236fa" = 1756,
  "#1757 HFC-32" = 1757,
  "#1758 Other ODSS" = 1758)
```

### Emissions

#### Introduction {-}

Ozone-depleting substances (ODS) are being phased out under the terms of the Montreal Protocol and the 1990 Clean Air Act Amendments. ODS include chlorofluorocarbons (CFC’s), hydrochlorofluorocarbons (HCFC’s), carbon tetrachloride, etc., and have been used in refrigeration and air conditioning equipment, solvent cleaning, foam production, sterilization, aerosol and fire extinguishing applications. The substitutes approved to replace the ODS include hydrofluorocarbons (HFC’s) and perfluorocarbons (PFC’s) emit both total organic gases (TOG) and greenhouse gases (GHG’s), many of which have high global warming potentials (GWP’s). All of the ODS Substitutes are non-reactive, so there are no reactive organic gas (ROG) emissions. The use of these ODS substitutes have steadily increased since 1990.

#### Methodology {-}

The TOG and GHG emissions were estimated using California Air Resources Board’s (CARB’s) Documentation of California’s Greenhouse Gas Inventory (6th Edition, updated August 1, 2013) data. CARB emission totals represented values for the entire state and were divided into 4 sectors (commercial, industrial, residential and transportation). Within each sector, the ODS Substitutes were further divided by usage (i.e. Aerosols, Fire Protection, Foams, Refrigeration and Air Conditioning, and Solvents, if applicable). The District’s portion of the State’s total was estimated by comparing 2011 data in Table B-3 (Total Population of California Counties), Table C-4 (“Wage and Salary Workers in Nonagricultural Establishments By Industry, California”) and Table C- 7 (“Wage and Salary Workers in Nonagricultural Establishments By Industry, California Metropolitan Areas”) of the California Department of Finances Statistical Abstract. For the residential sector, the population in the Bay Area District counties was compared to the State population. The number of Bay Area workers in the industrial, commercial, and transportation sectors were compared to the number of state workers in these sectors. In 2011, the fraction of Bay Area population and workers to that of State population and workers in the residential, industrial, commercial, and transportation sectors were 0.19, 0.14, 0.23, and 0.18, respectively. Each ODS Substitute, depending upon sector, was multiplied by this fraction and the State value.

```{r misc_other-ODSS-emission_factors-table, include=FALSE, eval=FALSE}
BY2011_annual_area_source_emission_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_emission_factors(
    pollutants = c(
      BY2011_POLLUTANTS, 
      "HFC+PFC"))
```


#### Monthly Variation {-}

Monthly variation of emissions for these categories is assumed to be uniform throughout the year.

#### County Distribution {-}

The county distributions for these categories were based on Association of Bay Area Government’s (ABAG) 2009 Projections Data for 2011. For those emissions in the commercial, industrial, residential, and transportation sectors, ABAG’s data from retail employment, manufacturing and wholesale employment, population, and transportation and utility employment, respectively, were used. Each category may have a combination of aforementioned sectors, so a composite county fraction was calculated based on the sector’s emission (within the category).

### Trends

#### History {-}

```{r misc_other-ODSS-annual_emissions-chart, fig.height=5, out.height=500}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

Emission data from 1990 – 1999 was based on trend data from CARB’s 1990 – 2004 GHG Inventory by IPCC Category. Emission data from 2000 - 2010 was based on emission data from CARB’s 2000 – 2011 GHG Inventory by IPCC Category.

#### Growth {-}

**FIXME: Double-check whether these are consistent with the year-over-year changes in emissions (shown in figure above). BY2011 throughputs for these categories were not recorded in DataBank. **

```{r misc_other-ODSS-annual_growth-chart, fig.height=12, out.height=1200}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = category) 
```

Emission data from 2012 – 2030 was based on trend data from CARB’s California GHG Emissions – Forecast (2008 – 2020), (last updated October 28, 2010).

***

By: Stuart Schultz 
Date: February 2014 
Base Year 2011
