## Paved Roads {#misc_other-roads-paved}

```{r misc_other-roads-paved-setup}
THESE_CATEGORIES <- c(
  "#1759 Paved Freeways" = 1759,
  "#1760 Paved Major Roads" = 1760,
  "#1761 Paved Collectors" = 1761,
  "#1762 Paved Local Streets" = 1762)
```

### Emissions

#### Introduction {-}

Fugitive dust particles raised from the movements of motor vehicles on paved road surfaces are included in this category.

#### Methodology {#misc_other-roads-paved-methodology -}

The methodology for estimating particulate emissions from vehicular travel on paved roads was updated in the Final Section of Fifth Edition of U.S. EPA’s Compilation of Air Pollutant Emission Factors AP42 document, Volume I, Chapter 13.2.1.

The methodology was adapted and refined for California by CARB. For a full description of this methodology and references, please see CARB’s methodology document “2013 Update_7 9 PavedRds Meth.pdf”.

A brief description is given below:

Emission rates are a function of vehicle weight and silt loading as shown in the following equation:

$$
E = k \left(\frac{sL}{2}\right)^{0.91} \times \left(\frac{W}{3}\right)^{1.02} \times \left(1 - \frac{P}{4N}\right)
$$
where: 

<div class="nobullet">

- $E$ is the particulate emission factor in grams per vehicle miles traveled (VMT);

- $k$ is the particle size multiplier used to compute PM10 and PM2.5 (1.0 and 0.25 grams/mile respectively);

- $sL$ is the roadway silt loading in grams per square meter;

- $W$ is the average vehicle weight in tons;

- $P$ is the number of "wet" days with at least 0.254 mm (0.01") of precipitation; and

- $N$ is the number of days in the averaging period, 365 for yearly or 30 for monthly.
 
</div>

California specific silt loading for different road types were measured in a study carried out by Midwest Research Institute (MRI) in 1995. Roads were divided into four classes with the corresponding silt loading factors ($g/m^2$):

<div style="width: 50%; padding-left: 25%">

| Road Type              |         sL |
|:-----------------------|-----------:|
| Freeway/Expressway     |       0.02 |
| Major Street/Collector |      0.032 |
| Local Street           |       0.32 |
| Rural                  |        1.6 |

</div>

Average vehicle weight ($W$) was assumed to be 2.4 tons, based on vehicle counts performed during the MRI study.
Estimated fraction of county VMT in each of the four roadway types were taken from 2008 data by Highway Performance Monitoring Systems (HPMS). County specific 2011 VMT data were taken from California Air Resources Board EMFAC2011-SG model.

Number of wet days ($N$) for each county was derived from the most appropriate meteorological station for that county.

The monthly fraction of annual VMT came from monthly Caltrans VMT highway data prepared for the Sacramento Office of the Federal Highway Administration. These were combined with the number of wet days in the relevant month to develop a monthly profile.

### Trends

#### History {-}

```{r misc_other-roads-paved-annual_emission-chart, fig.height=12, out.height=1200}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

In previous base years, emissions from paved road dust travel were assumed to grow proportionally with VMT. According to this assumption, Bay Area road dust emissions should have increased by 30% between 1990 and 2011 based on growth in VMT. Ambient air monitoring data and chemical mass balance analysis do not show this trend.

#### Growth {- #misc_other-roads-paved-growth}

```{r misc_other-roads-paved-annual_growth-chart, fig.height=6, out.height=600}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

It is believed that re-suspension of road dust quickly reaches an equilibrium condition. Thus, CARB proposed that instead of using VMT as a surrogate for growth, roadways center line miles (CLM) are used. MTC’s CLM data show an increase of less than 2% for the same period (less than 0.1% per year), and this was used to create trends around the 2011 base year emissions.

***

By: A. K. Fanai 
December 2013
Base Year 2011
