## Sanitary Sewers

```{r misc_other-sanitary_sewers-setup}
THESE_CATEGORIES <- c(
  "#761 Sanitary Sewers" = 761)
```

### Emissions

#### Introduction {-}

This category includes organic compounds emissions from sanitary sewer lines in industrialized areas leading to sewage treatment plants. This category also includes waste material generated from portable or semi-permanent toilets and discharged to the sanitary sewer system.

#### Methodology {-}

A report on "Evaluation of Emissions from Selected Uninventoried Sources in the State of California", by R. Dickson; W.R. Oliver, and S. Tate showed an estimate of discharged material to the sewer systems in the United States. This estimate of national loading to sewers was adjusted for the Bay Area. In the report, about 50% of volatile organic compounds (VOC) was assumed from the discharged material volatilizes in the sewer prior to becoming influent to treatment plants. It was further assumed that 50% of the volatilized materials have already been accounted for in other categories, such as cleanup solvent.

An emission factor of 250 lbs of organics per thousand pounds of industrial sewer loading was also developed based on the above report. The VOC Emissions are calculated by multiplying the throughput data with the emission factor.

#### Monthly Variation {-}

Monthly distribution was estimated based on estimated load throughout the year.

#### County Distribution {-}

The county population was used to distribute emissions into each county.

### Trends

#### History {-}

```{r misc_other-sanitary_sewers-annual_emission-chart, fig.height=5, out.height=500}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

Emissions through the years were estimated by using historical data on household population.

#### Growth {-}

```{r misc_other-sanitary_sewers-annual_growth-chart, fig.height=4, out.height=400}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

ABAG’s 2009 Projections Household Population profile was utilized to project future emissions to year 2030.

***

By: Michael Nguyen 
Date: January, 2014 
Base Year 2011
