## Farming Operations

```{r misc_other-farming-setup}
THESE_CATEGORIES <- c(
  "#749 Agricultural Land Preparation" = 749,
  "#1435 Agricultural Harvest Operations" = 1435)
```

### Emissions

#### Introduction {-}

Farming Operations consist of two categories, Agricultural Land Preparation (Category 749) and Agricultural Harvest Operations (Category 1435). The methodology for emission calculation and temporal activity for both these categories were taken from the California Air Resources Board’s (ARB’s) Emission Inventory Procedural Manual Section 7.4 (Agricultural Land Preparation, revised January 2003) and Section 7.5 (Agricultural Harvest Operation, revised January 2003).

Category 749 accounts for particulate emissions generated by farming operations such as tilling, plowing, discing, leveling, etc. These activities are normally performed in the early spring and/or fall months. Therefore, particulate emissions from agricultural tilling are highly dependent on type of crop, climate, soil properties and equipment characteristics.

Category 1435 accounts for particulate emissions caused from harvest activities. These activities include harvest vehicles traveling over the soil, mechanical processing of crop and underlying soil, or removal of crop waste material through blowing or sweeping action. As of this writing, the only crops in California that had harvest particulate emissions factors were almonds, cotton, and wheat. All other relevant crops are assigned emission factors by scaling from these three measured values.

Emissions from fuel combustion of agricultural equipment, such as mowers, tractors, tillers, etc., are accounted for in Category 1655 (Agricultural Equipment, Gasoline-4 Stroke), Category 1656 (Agricultural Equipment, Evaporative-4 Stroke), and Category 1646 (Agricultural Equipment, Diesel).

#### Methodology {-}

##### Category 749 {#cat_749-methodology -}

Agricultural land preparation particulate emissions for each crop are estimated using the following equation:

$$
\text{Emissions}_{crop} = \text{Emission Factor}_{crop} * \text{Acres}_{crop}
$$

The crop specific PM10 emission factors are calculated by multiplying a land preparation emission factor (i.e. root cutting, discing, rippling, weeding, land planning, etc.) with the number of passes performed per acre that are needed to prepare a field for planting a particular crop (acre-pass). A crop may have multiple land preparation operations with its corresponding number of acre-passes. In this case, the crop specific emission factor is the sum of acre-pass weighted emission factor for each land preparation operation. For example, the crop PM10 emission factor for garlic is as follows:

**FIXME: RECREATE TABLE**

There are 21 crop specific PM10 emission factors (see Table 2.a of ARB’s Agricultural Land Preparation document) that include such crops as alfalfa, almonds, garlic, grapes (raisin, table and wine), tomatoes, wheat, etc. All other crops are assigned an emission factor from one of the 21 crop specific PM10 emission factors (see Table 3 of ARB’s Agricultural Land Preparation document).

**Example 1:** Calculate the 2010 PM10 and total particulate emissions from land preparation activities for garlic in Santa Clara County, where

a. the crop specific PM10 emission factor = 6.5 lbs PM10/acre/yr, 
b. 366 acres were devoted to garlic in 2010, and
c. the PM10 factor is .4543.

$$
\begin{eqnarray}
\text{PM}_{10}\ \text{emissions} &=& \frac{6.5\ lb}{acre \cdot yr}\times 366\ acre \\
  &=& 2379\ lb/yr \\
  &=& 1.19\ ton/yr\ \text{PM}_{10}
\end{eqnarray}
$$

$$
\begin{eqnarray}
\text{PM emissions} &=& 1.19\ ton/yr\ \text{PM}_{10} \div 0.4543 \\
  &=& 2.62\ ton/yr\ \text{PM}
\end{eqnarray}
$$
Each of the county’s crops are estimated in this fashion and then summed for the total PM10 emissions. The nine counties within the Bay Area were summed to get the District total. (The District’s portion of Solano and Sonoma Counties were 38% and 32%, respectively.) PM emissions are calculated by dividing PM10 value by 0.4543.

##### Category 1435 {-}

Agricultural Harvest Operations particulate emissions for each crop are estimated using the following equation:

$$
\text{Emissions}_{crop} = \text{Emission Factor}_{crop} * \text{Acres Harvested}_{crop}
$$

The individual crop emissions for each county were summed to produce county and District wide total particulate and PM10 agricultural harvest emissions. The PM10 emission factors were taken from Table 2 of ARB’s Agricultural Harvest Operations document. Using the PM10 emissions factors for cotton, almonds, and wheat as a baseline, other crop’s PM10 emission factors were estimated. The number of acres to each applicable crop was obtained from either the county’s annual agricultural crop reports or the California Agricultural Statistics Service (CASS).

Example 2: Calculate the 2010 PM10 and total particulate emissions from agricultural harvest operations for walnuts in Contra Costa County, where

a. the Crop specific PM10 emission factor = 40.77 lbs PM10/acre, 
b. 399 acres were devoted to walnuts in 2010, and
c. the PM10 factor is .4543.

$$
\begin{eqnarray}
\text{PM}_{10}\ \text{emissions} &=& \frac{40.77\ lb}{acre \cdot yr}\times 399\ acre \\
  &=& 16267\ lb/yr \\
  &=& 8.13\ ton/yr\ \text{PM}_{10}
\end{eqnarray}
$$

$$
\begin{eqnarray}
\text{PM emissions} &=& 8.13\ ton/yr\ \text{PM}_{10} \div 0.4543 \\
  &=& 17.90\ ton/yr\ \text{PM}
\end{eqnarray}
$$

Each of the county’s crops are estimated in this fashion and then summed for the total PM10 emissions. The nine counties within the Bay Area were summed to get the District total. (The District’s portion of Solano and Sonoma Counties were 38% and 32%, respectively.) PM emissions are calculated by dividing PM10 value by 0.4543.

#### Monthly Variation {-}

The monthly variations of emissions for the Bay Area counties in Category 749 were based on the ARB’s seasonal profile for agricultural land preparation emissions (Table 6, Agricultural Land Preparation, Section 7.4). For Category 1435, the monthly variations of emissions were based on ARB’s seasonal profile for agricultural harvest emissions (Table 4, Agricultural Harvest Operations, Section 7.5).

#### County Distribution {-}

For both categories, the county distribution was based on the crop activity reported by the counties’ annual agricultural crop reports or the CASS.

### Trends

#### History {-}

```{r misc_other-farming-annual_emissions-chart, fig.height=8, out.height=800}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

For Category 749, the historical growth profile was based on a combination of prior emissions data (back to 1987) and an annual activity increase factor of 1.00862 from 1986 back to 1967. This backcasting value represented the Bay Area’s annual activity increase (in acres) from 2010 going back to 1987.)

For Category 1435, the historical growth profile was based on a combination of prior emissions data (back to 1987) and an annual activity increase factor of 1.00905 from 1986 back to 1967. This backcasting value represented the Bay Area’s annual activity increase (in acres) from 2010 going back to 1987.)

#### Growth {-}

```{r misc_other-farming-annual_growth-chart, fig.height=4, out.height=400}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

Projected emissions to 2030 for both categories were based on ARB’s growth profile for Agricultural Operations. For the Bay Area, this amounts to a 0.1% decrease in activity per year.

For Categories 749 and 1435, the projected growth profile was based on emissions data from 2000 – 2010. The annual activity factors during this time period decreased by 0.004692 and 0.004777 per year, respectively.

***

By: Stuart Schultz 
Date: January 2014 
Base Year 2011
