## Cogeneration {#SS-combust-cogen}

```{r SS-combust-cogen-setup}
THESE_CATEGORIES <- c(
  "#290 Boilers" = 290,
  "#291 Turbines" = 291,
  "#292 Reciprocating Engines" = 292)
```

### Emissions

#### Introduction {-}

These stationary combustion categories (290, 291 and 292) account for criteria pollutant (particulate, organic, NO~x~, SO~x~, and CO) and greenhouse gas emissions (CO~2~, CH~4~, and N~2~O) from boilers, turbines, and reciprocating engines at cogeneration plants in the San Francisco Bay Area. Cogeneration plants are located at many sites in the Bay Area, including oil, chemical and food processing companies, municipal utility companies, hospitals, and military bases etc.

Cogeneration plant is a power station that simultaneously generates both electricity and useful heat by utilizing one primary fuel.

Modern, highly efficient power plants use the gas turbine Combined Cycle (CC). The combined-cycle gas turbine power plant consists of one or more gas turbines equipped with heat recovery steam generators to capture heat from the gas turbine exhaust. Steam produced in the heat recovery steam generators powers a steam turbine generator to produce additional electric power. Use of the otherwise wasted heat in the turbine exhaust gas results in high thermal efficiency compared to other combustion based technologies. Combined-cycle plants currently entering service can convert about 50 percent of the chemical energy of natural gas into electricity. Additional efficiency can be gained in combined heat and power (CHP) applications (cogeneration), by bleeding steam from the steam generator, steam turbine or turbine exhaust to serve direct thermal loads, such as food and chemical processing.

#### Methodology {-}

Emissions for these categories were obtained from point source data only, as contained in the District's data bank. The District updates the data each year on a source-by-source basis using as input:

1. Process material throughputs as reported by the plants

2. Emissions factors (these may be source specific factors reported by the plants through source test results or applicable general factors, i.e. from the U.S. Environmental Protection Agency (EPA))

3. Emissions control factors (device-specific or general - these may be supplied by the plants also)

Information on these specific cogeneration sources allowed them to be identified as boilers, turbines or reciprocating engines. Some of these sources may be of the "dual fuel" type, i.e., they are able to combust either gaseous or liquid fuel. EPA's document AP-42 contains emissions information on these types of sources.

The fuel specific greenhouse gas emission coefficients for these categories were obtained from the U.S. Department of Energy’s (DOE’s) Energy Information Administration (EIA), the U.S. Environmental Protection Agency’s (EPA’s) document AP-42, and the California Energy Commission (CEC).

#### County Distribution {-}

The Bay Area Air District’s point source database contains county distribution information for each facility based on its location.

#### Monthly Variation {-}

Monthly variation of emissions is based on the company reported quarterly throughput/ activity data.

### Trends {#SS-combust-cogen-trends}

#### Historical {-}

```{r SS-combust-cogen-emission-chart, fig.height=18, out.height=1800}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

```{r SS-combust-cogen-BY-vs-DB-chart, fig.height=18, out.height=1800}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY_vs_DB_point_source_annual_emissions()
```

Historical emissions have varied with fuel usage activity. Prior to Base Year 1987, these three categories were grouped as one category.

#### Growth {-}

```{r SS-combust-cogen-growth-chart, fig.height=8, out.height=800}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

Projections for categories 290, 291, and 292 were developed based on the following methods in combination with the CEC’s forecasts for the combined heat and power generation demand.

For Category #290 (boilers), it was assumed that annual emissions, over the years, would tend to follow two components: retail trade industry employment and services industry employment. As such, the annual variation ratio value was developed as a hybrid, based on 50% of the retail trade industry employment value and 50% of the services industry employment value.

For Category #291 (turbines), it was assumed that annual emissions, over the years, would tend to follow two components: manufacturing industry employment and population within the District jurisdiction. As such, the annual variation ratio value was developed as a hybrid, based on 50% of the manufacturing industry employment value and 50% of the population value.

For Category #292 (reciprocating engines), it was assumed that emissions over the future years would tend to follow population growth.

The employment and population data used were obtained from two sources, the Association of Bay Area Government's (ABAG’s) 2009 "Projections" reports and the California Statistical Abstracts.

#### Control {-}

```{r SS-combust-cogen-control-chart, fig.height=6, out.height=600}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant)
```

District Regulation 9, Rules 8 and 9 control NO~x~ and SO~x~ emissions from the internal combustion of fuels in engines and turbines, respectively.

***

By: Sukarn Claire 
Date: January 2014 
Base Year: 2011
