## Back-up Diesel Generator

```{r SS-combust-engines-crisis-setup}
THESE_CATEGORIES <- c(
  "#1598 Emergency Diesel Generators" = 1598)
```

### Emissions

#### Introduction {-}

Category 1598 and 304 contain emissions from diesel engines used in emergency/standby electric generators. Category 1598 was added to account for additional emissions generated due to the increased use of emergency generators during the electric power shortage crisis in California (2001-2002). Category 304 contains emissions from normal usage of standby generators. These emissions from Category 304 are not covered here.

#### Methodology {-}

Emissions due to increased emergency generator usage were estimated to be negligible during the electric power shortage crisis in California (2001-2002) and emissions are not expected to grow in the near future.
The District collects fuel usage data each year on a source-by-source basis from facilities operating in the Bay Area. Emissions are calculated using fuel usage data and emission factors in the database. Emission and control factors used are either source specific as reported by the plants or general factors, i.e., from the Environmental Protection Agency (EPA); the U.S. Department of Energy’s (DOE’s) Energy Information Administration (EIA); California Energy Commission (CEC) etc.

### Trends

#### History {-}

```{r SS-combust-engines-crisis-annual_emission-chart, fig.height=8, out.height=800}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

#### Growth {-}

```{r SS-combust-engines-crisis-growth-chart}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

An electric energy crisis in California appears to be over. Emissions from increased usage of standby generators did not appear to materialize as estimated previously.

#### Control {-}

Regulation 9 controls emissions of NO~x~ and SO~x~ of combustion.

***

By: Sukarn Claire 
Date: January 2014 
Base Year: 2011
