## Domestic Natural Gas

```{r SS-combust-domestic-NG-setup}
THESE_CATEGORIES <- c(
  "#283 Space Heating" = 283,
  "#284 Water Heating" = 284,
  "#285 Cooking" = 285, "#2540 Other" = 2540)
```

### Emissions

#### Introduction {-}

These categories estimate criteria pollutant (particulate, organic, NO~x~, SO~x~, and CO) and GHG emissions (CO~2~, CH~4~, and N~2~O) resulting from the combustion of natural gas in the residential sector. Natural gas consists of a high percentage of methane (generally above 85 percent) and varying amounts of ethane, propane, butane, and inert gases. The combustion of natural gas in the residential sector is broken down into four categories: Space Heating, Water Heating, Cooking, and Other. Categories 283, 284, 285, and 2540 account for area source emissions from Space Heating, Water Heating, Cooking, and Other, respectively.  The unspecified category, Other, includes the combustion of natural gas in appliances such as clothes dryers, barbecues, and water heaters used for pools, spas and hot tubs.
Design of residential boilers and furnaces generally resemble fire tube type boilers with flue gas traveling through several channels or tubes with water or air circulated outside the channels or tubes.

#### Methodologies {-}

The residential natural gas consumption data by county for these categories was obtained from the California Energy Commission (CEC) fuel consumption data base.  The natural gas consumption was broken down into each use category based on information from CEC and PG&E, and is shown below.

```{r SS-combust-domestic-NG-apportionment-table}
table_data <-
  tribble(
    ~ "Category", ~ "Percent",
    "#283 Space Heating", 50.34,
    "#284 Water Heating", 41.15,
    "#285 Cooking", 4.47, "#2540 Other", 4.04)

table_data %>%
  mutate_at(
    vars(Percent),
    ~ formattable::percent(. / 100, digits = 1)) %>%
  kable_BY2011(
    caption = "Apportionment of NG throughput.")
```

Emission factor information for natural gas combustion was obtained from the U.S. Environmental Protection Agency's (EPA's) document AP-42, the U.S. Department of Energy's (DOE's) Energy Information Administration (EIA) and the California Energy Commission (CEC).

The natural gas combustion emission factors for these categories, in pounds per million cubic feet (Lb/MMCF) are shown below in Table \@ref(tab:SS-combust-domestic-NG-emfac-table).

```{r SS-combust-domestic-NG-emfac-table}
BY2011_annual_area_source_emission_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  filter_years(
    CY(2011)) %>%
  kable_BY2011_emission_factors(
    pollutants = union(
      BY2011_POLLUTANTS,
      c("CO2", "CH4", "N2O")),
    caption = "Emission factors (lb/MMCF).")
```

#### County Distribution {-}

Natural gas information provided by CEC and PG&E includes residential, commercial, and industrial usage for the Bay Area nine counties by month. Information on Palo Alto's natural gas usage was obtained separately from the City of Palo Alto and was used together with Santa Clara County natural gas usage values. This was done because the city obtained gas from a supplier other than PG&E. Solano and Sonoma Counties are partially in the San Francisco Bay Area Air District, so data were used for the cities that are in the District. For Solano County, data used were for Benicia, Fairfield, Suisun and Vallejo; for Sonoma County, data used were for Cotati, Petaluma, Rohnert Park, Santa Rosa, Sebastopol and Sonoma.

```{r SS-combust-domestic-NG-county-fraction-table}
BY2011_county_fraction_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_county_fractions()
```

#### Temporal Variation {-}

*Space Heating*

- Daily Activity: The maximum activity occurs in the early daylight hours and in the evening hours, with average activity during the day and low activity at night.

- Weekly Activity Code: The activity is uniform seven days a week.

- Monthly Activity: The monthly activity was based on monthly residential natural gas sales from the California Energy Commission. Activity occurs from November to June, with the highest months being December through April.

*Water Heating*

- Daily Activity: The maximum activity occurs in the early daylight hours and in the evening hours, with average activity during the day and low activity at night.

- Weekly Activity: The activity is uniform seven days a week.

- Monthly Activity: The monthly activity is assumed to be uniform throughout the year. 

*Cooking*

- Daily Activity: The activity occurs during meal time hours.

- Weekly Activity: The activity is uniform seven days a week.

- Monthly Activity: The monthly activity is assumed to be uniform throughout the year.

### Emission Trends

#### History {-}

```{r SS-combust-domestic-NG-emission-chart, fig.height=18, out.height=1800}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

Historical emission trends are based on natural gas usage in the San Francisco Bay Area.

#### Growth {-}

```{r SS-combust-domestic-NG-growth-crosswalk}
BY2011_growth_profile_crosswalk %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_growth_crosswalk()
```

```{r SS-combust-domestic-NG-growth-chart, fig.height=6, out.height=600}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

Emission growth projections are based on household population growth in combination with CEC's forecasts for residential sector natural gas demand. Household population data was obtained from two sources, the Association of Bay Area Government's (ABAG's) 2009 "Projections" reports and the California Statistical Abstracts.

#### Control {-}

```{r SS-combust-domestic-NG-control-chart, fig.height=3, out.height=300}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant) 
```

The District adopted [Rule 9-6] on April 1, 1992 to control the amount of NO~x~ emissions from natural gas fired water heaters. This rule has a control of 46% with a rule effectiveness of 94% reached by the year 2002.

***

By: Sukarn Claire 
Date: January 2014 
Base Year: 2011
