## Turbines {#SS-combust-turbine}

```{r SS-combust-turbine-setup}
THESE_CATEGORIES <- c(
  "#305 Gas Fired Turbines" = 305,
  "#306 Oil Fired Turbines" = 306)
```

### Emissions

#### Introduction {-}

Categories 305 and 306 account for criteria pollutant (particulate, organic, NO~x~, SO~x~, and CO) and greenhouse gas emissions (CO~2~, CH~4~, and N~2~O) from fuel combustion in turbine engines in the San Francisco Bay Area. Category 305 accounts for emission from gas fired turbines and Category 306 from oil fired turbines, respectively.

A combustion turbine is a rotary engine that extracts energy from a flow of combustion gases. It has an upstream compressor coupled to a downstream turbine, and a combustion chamber in-between. The products of the combustion are forced into the turbine section. There, the high velocity and volume of the gas flow is directed through a nozzle over the turbine's blades, spinning the turbine which powers the compressor and drives their mechanical output.

#### Methodologies {-}

Emissions for these categories were obtained from point source data as found in the District's Data Bank System. Each year, the District collects and records the data from individual plants via a permitting process. The data is entered and recorded as follows:

1. Process material throughput/activity (as reported by the plants, this data is routinely updated)

2. Emission factors (these may be source specific as reported by the plants or general factors, i.e. from the EPA)

3. Emission control factors (device-specific or general - these may be supplied by the power plants also)

Specific information on these sources allowed them to be identified as either gas or liquid fuel fired turbines. The EPA's document AP-42 contains this information on various fuel combusting turbines and engines.

The fuel specific greenhouse gas emission coefficients for these categories were obtained from the U.S. Department of Energy’s (DOE’s) Energy Information Administration (EIA), the U.S. Environmental Protection Agency’s (EPA’s) document AP-42, and the California Energy Commission (CEC).

#### County Distribution {-}

The District’s point source database contains county distribution information for each facility/source based on its location.

```{r SS-combust-turbine-county-fraction-table}
BY2011_county_fraction_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_county_fractions()
```

#### Monthly Variation {-}

Monthly variation of emissions is based on company reported quarterly throughput or activity data.

### Trends {#SS-combust-turbine-trend}

#### History {-}

```{r SS-combust-turbine-emission-chart, fig.height=12, out.height=1200}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

```{r SS-combust-turbine-BY-vs-DB-chart, fig.height=18, out.height=1800}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY_vs_DB_point_source_annual_emissions()
```

For category #306, it was felt that historical emission trends tend to follow population data. As such, the annual variation ratio value for each year was based on the appropriate population value.

#### Growth {-}

```{r SS-combust-turbine-growth-chart, fig.height=8, out.height=800}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

For Category #305, it appeared that sources at oil refineries made the greatest contribution to emissions. Therefore, the emission growth profile for this category is developed in the same manner as the oil refinery external combustion categories. This category is projected to grow at about 1 percent per year.

Growth profile for Category #306 is assumed to follow population growth. The population data was obtained from the Association of Bay Area Government's (ABAG’s) 2009 projection reports.

#### Control {-}

```{r SS-combust-turbine-growth-crosswalk}
BY2011_growth_profile_crosswalk %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_growth_crosswalk()
```

```{r SS-combust-turbine-control-chart}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant) 
```

The Air District’s Regulation 9, Rule 9 controls NO~x~ and SO~x~ emissions from fuel combustion in stationary turbines.

***

By: Sukarn Claire 
Date: January 2014 
Base Year: 2011
