## Other External Combustion - Natural Gas {#SS-combust-external-NG}

```{r SS-combust-external-NG-setup}
THESE_CATEGORIES <- c(
  "#307 NG Combustion (Point, Misc)" = 307,
  "#1590 NG Combustion (Industrial)" = 1590,
  "#1591 NG Combustion (Commercial)" = 1591,
  "#968 NG Combustion (Glass Furnace)" = 968)
```

### Emissions

#### Introduction {-}

Categories 307, 968, 1590, and 1591 account for criteria pollutant (particulate, organic, NO~x~, SO~x~, and CO) and greenhouse gas emissions (CO~2~, CH~4~, and N~2~O) from natural gas combustion sources.

Categories 307, 1590, and 1591 estimate emissions from sources, such as industrial/commercial/institutional water and steam boilers, furnaces, space heaters, process heaters, pre heaters, ovens and after burners etc.

Category 968 accounts for emissions from the natural gas fired glass melting furnaces at glass manufacturing plants in the Bay Area.

#### Methodologies {-}

##### Point source {-}

Emissions for Categories 307 and 968 were obtained from point source data only as found in the District's data bank. The District updates the data each year on a source-by-source basis using as input:

1. Process material throughputs as reported by the plants.

2. Emissions factors (these may be source specific as reported by the plants or general factors, i.e. from the EPA).

3. Emissions control factors (device-specific or general - these may be supplied by the plants also).

Information on these specific sources allowed them to be identified as boilers, heaters, and furnaces etc. EPA's document AP-42 contains combustion related emissions information on these sources.

The fuel specific greenhouse gas emission coefficients for these categories were obtained from the U.S. Department of Energy’s (DOE’s) Energy Information Administration (EIA), the U.S. Environmental Protection Agency’s (EPA’s) document AP-42, and the California Energy Commission (CEC).

##### Area source {-}

Emissions for categories 1590 and 1591 were obtained from the area sources only. Categories 1590 and 1591 contain emissions from industrial and commercial sources, respectively. The area source natural gas usage estimates were developed by obtaining the total point source usage, and then subtracting it from the corresponding combined values for commercial, institutional and industrial natural gas total usage (point + area) in the District, provided by the California Energy Commission (CEC) or PG&E. The computation to develop area source natural gas usage was as follows:

\begin{align}

    \text{CEC or PG&E's total natural gas usage values} & \\
– \text{District Data Bank's Point source usage values} & \\

\hline

          = \text{Area source natural gas usage values} &

\end{align}

Emission factor information for natural gas combustion was obtained from the U.S. Environmental Protection Agency’s (EPA's) document AP-42, the U.S. Department of Energy’s (DOE’s) Energy Information Administration (EIA) and the California Energy Commission (CEC).

The area source natural gas combustion emission factors in pounds per million cubic feet (Lb/MMCF) are shown below.

```{r SS-combust-external-NG-emfac-table}
BY2011_annual_area_source_emission_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_emission_factors(
    pollutants = union(
      BY2011_POLLUTANTS, 
      c("CO2", "CH4", "N2O")),
    caption = "Emission factors (lb/MMcf).")
```

#### County Distribution {-}

Categories 307 and 968: The District’s point source database contains county distribution information for each facility based on its location.

Categories 1590 and 1591: County distribution is based on natural gas usage in each of the Bay Area County.

```{r SS-combust-external-NG-county-fraction-table}
BY2011_county_fraction_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_county_fractions()
```

#### Monthly Variation {-}

For point sources monthly variation of emissions is based on company reported quarterly throughput data. Area source monthly variation is based on average fuel usage by month.

### Trends

#### History {-}

```{r SS-combust-external-NG-emission-chart, fig.height=12, out.height=1200}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

```{r SS-combust-external-NG-BY-vs-DB-chart, fig.height=18, out.height=1800}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY_vs_DB_point_source_annual_emissions()
```

Glass Melting Furnaces, Category 968 was added to the emissions inventory system for base year 1990 after adoption of [Regulation 9-12]. Prior to base year 1990, emissions from Glass Melting Furnaces were accounted for in Category 307. For base year 2002, Category 307 was further split into point sources (C307) and area sources (C1590). For base year 2008, Category 1590 was split into Industrial (C1590) and Commercial (C1591) sources.

Prior to base year 1987, category 307 was grouped as four categories: #86, 97, 99 and 111. This change to a single category for all area sources was made due to unavailability of separate natural gas usage data for each category.

#### Growth {-}

```{r SS-combust-external-NG-growth-crosswalk}
BY2011_growth_profile_crosswalk %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_growth_crosswalk()
```

```{r SS-combust-external-NG-growth-chart, fig.height=6, out.height=600}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

Growth projections for Category 307, 1590 and 1591 are based on the California Energy Commission’s natural gas demand forecasts.

For category 968, it was assumed that annual emissions would tend to follow and be influenced by manufacturing industry employment.

The data used in developing growth profile was obtained from the Association of Bay Area Government's (ABAG’s) 2009 "Projections" reports.

#### Control {-}

```{r SS-combust-external-NG-control-chart, fig.height=6, out.height=600}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant) 
```

District’s [Regulation 9] controls emissions of NO~x~ and CO from combustion.

***

By: Sukarn Claire 
Date: January 2014 
Base Year: 2011
