## Other External Combustion - All Other Fuels {#SS-combust-external-other}

```{r SS-combust-external-other-setup}
THESE_CATEGORIES <- c(
  "#308 LPG" = 308,
  "#309 Distillate Oil" = 309,
  "#310 Residual Oil" = 310,
  "#311 Coke, Coal" = 311,
  "#312 Other Fuels" = 312)
```

### Emissions

#### Introduction {-}

These categories account for criteria pollutant (particulate, organic, NO~x~, SO~x~, and CO) and greenhouse gas emissions (CO~2~, CH~4~, and N~2~O) from external combustion of fuels other than natural gas at industrial facilties in the San Francisco Bay Area. Categories 308, 309, 310, 311, and 312 estimate emissions from external combustion of fuels such as liquefied petroleum gas (LPG), distillate oil, residual oil, coke & coal and other fuels, respectively.

#### Methodologies {-}

Emissions for these categories were obtained from point source data only, as contained in the District's data bank. The District updates the data each year on a source-by-source basis using as input:

1. Process material throughputs as reported by the plants utilizing these fuels for external fuel combustion

2. Emissions factors (these may be source specific factors reported by the plants through source test results or applicable general factors, i.e. from the EPA)

3. Emissions control factors (device-specific or general - these may supplied by the plants also)

Information on these specific sources allowed them to be identified as using fuels such as liquefied petroleum gas (LPG), distillate oil, residual oil, coke & coal and other fuels. Environmental Protection Agency’s document AP-42 contains external combustion emission information on these types of sources.

The fuel specific greenhouse gas emission coefficients for these categories were obtained from the U.S. Department of Energy’s (DOE’s) Energy Information Administration (EIA), the U.S. Environmental Protection Agency’s (EPA’s) document AP-42, and the California Energy Commission (CEC).

The county, month, and day factors are obtained from the data bank's information on each plant's location, seasonal usage, and days per week of operation.

```{r SS-combust-external-other-county-fraction-table}
BY2011_county_fraction_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_county_fractions()
```

### Trends

#### History {-}

```{r SS-combust-external-other-emission-chart, fig.height=12, out.height=1200}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

Emissions prior to 1987 were derived from Base Year 1983 trend values. Category 309 had been grouped as four categories before Base Year 1987 and Category 311 had been grouped as two categories. The historical trend values for categories 309 and 311 were summed, respectively, to build the historical emissions data.

#### Growth {-}

```{r SS-combust-external-other-growth-crosswalk}
BY2011_growth_profile_crosswalk %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_growth_crosswalk()
```

```{r SS-combust-external-other-growth-chart, fig.height=8, out.height=800}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

For Categories 308 and 309, it was felt that annual emissions, over the years, would tend to follow and be influenced in roughly equal amounts by two components as follow: manufacturing industry employment and services industry employment by county, all within the District jurisdiction. As such, the annual variation ratio value for each year, for each county involved, was developed as a hybrid, based on 50% of the appropriate county manufacturing industry employment value and 50% of the appropriate services industry employment value.

For Category #310, it was felt that annual emissions, over the years, would tend to follow and be influenced mainly by manufacturing industry employment by county, all within the District jurisdiction. As such, the annual variation ratio value for each year, for each county involved, was developed to follow the manufacturing industry employment value.

For Category #311, it was felt that annual emissions, over the years, would tend to follow and be influenced in roughly equal amounts by two components as follow: manufacturing industry employment and construction industry employment by county, all within the District jurisdiction. As such, the annual variation ratio value for each year, for each county involved, was developed as a hybrid, based on 50% of the appropriate county manufacturing industry employment value and 50% of the appropriate construction industry employment value.

For Category #312, it was felt that annual emissions, over the years, would tend to follow and be influenced in roughly equal amounts by two components as follows: one-third by manufacturing industry employment and two-thirds by population by county, all within the District jurisdiction. As such, the annual variation ratio value for each year, for each county involved, was developed as a hybrid, based on 33.3% of the county manufacturing industry employment value and 66.7% of the appropriate county population value.

The employment and population data used for the above growth profiles were obtained from two sources, the Association of Bay Area Government's (ABAG’s) 2009 "Projections" report and the "California Statistical Abstracts" document.

#### Control {-}

```{r SS-combust-external-other-control-chart, fig.height=8, out.height=800}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant) 
```

Regulation 9 controls emissions of NO~x~ and SO~x~ of combustion.

***

By: Sukarn Claire 
Date: January 2014 
Base Year: 2011
