## Gasoline Truck Loading {#petprod-gasoline-truck-load}

```{r petprod-gasoline-truck-load-setup}
THESE_CATEGORIES <- c(
  "#64 Bulk Plants" = 64,
  "#898 Bulk Terminals" = 898)
```

### Emissions

#### Introduction {-}

Fuels are delivered by tank trucks from the fuel terminals to service stations, commercial accounts and local bulk storage plants. Loading losses are primary source of evaporative emission from truck loading. Loading losses occur as organic vapors in the empty tank are displaced to atmosphere by the liquid being loaded into the tanks. These categories account for the organic emissions associate with transfer of gasoline to trucks from racks at terminals and bulk plants.

#### Methodologies {-}

These categories contain point source emissions. Emissions were determined by the District's Data Bank System. These data originated with information supplied by the plants and stored in the District's Data Bank System. Throughput is updated upon permit renewal. The organic liquid storage emission factors were obtained from AP-42.

#### Monthly Variation {-}

The Data Bank contains percentage of throughput data for each seasonal quarter: (December - February, March - May, June - August, September - October).

#### County Distribution {-}

Emissions distributed into the nine counties were based on the actual locations of the plants in the Bay Area.

```{r petprod-gasoline-truck-load-county-fraction-table}
BY2011_county_fraction_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_county_fractions()
```

### Trends {#petprod-gasoline-truck-load-trend}

#### History {-}

```{r petprod-gasoline-truck-load-emission-chart}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category)
```

Historical emission data was based on past years Bay Area gasoline consumption. The estimated gasoline consumption was obtained from California Taxable Gasoline Sales, Board of Equalization.

#### Growth {-}

```{r petprod-gasoline-truck-load-growth-crosswalk}
BY2011_growth_profile_crosswalk %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_growth_crosswalk()
```

```{r petprod-gasoline-truck-load-growth-chart}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr)
```

Projections are based on future gasoline consumption in the Bay Area.

#### Control {-}

```{r petprod-gasoline-truck-load-control-chart}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant)
```

Truck loading emissions were reduced due to the effect of [Rule 8-39], adopted on October 7, 1987 and [Rule 8-33], adopted on November 30, 1983. [Rule 8-33] requires to reduce emissions of precursor organic compounds from gasoline transfer operations at gasoline bulk terminals and delivery vehicles (Cat # 898). [Rule 8-39] requires to reduce emissions of precursor organic compounds from gasoline transfer operations at gasoline bulk plants and delivery vehicles (Cat # 64).

On April 15, 2009, the District amended [Rule 8-33] (Gasoline Bulk Terminals) and [Rule 8-39] (Gasoline Bulk Plants). The amendments include a requirement to minimize the release of organic compounds during maintenance and repair operations, and a reduction in the allowable backpressure in new vapor recovery system piping.

***

By: Michael Nguyen 
Date: January, 2014 
Base Year 2011

