## Refinery and Marine Loading Operations {#petprod-marine-load}

```{r petprod-marine-load-setup}
THESE_CATEGORIES <- c(
  "#60 Other Refinery Loading Operations" = 60,
  "#86 Lightering, Ships" = 86,
  "#87 Lightering, Barges" = 87,
  "#88 Ballasting, Crude Oil" = 88,
  "#89 Ballasting, Gasoline" = 89,
  "#90 Ballasting, Other Material" = 90,
  "#91 Vessel Cleaning & Gas Freeing" = 91,
  "#795 Tanker Loading, Crude Oil" = 795,
  "#796 Tanker Loading, Gasoline" = 796,
  "#797 Barge Loading, Crude Oil" = 797,
  "#798 Barge Loading, Gasoline" = 798,
  "#799 Tanker Loading, Crude Oil (Non-Refinery)" = 799,
  "#800 Tanker Loading, Gasoline (Non-Refinery)" = 800)

#
# Above, we have too many categories to fit on a single chart. 
# So that we can show an overview of emissions, here is a
# "consolidated" version of the above.
#
CONSOLIDATED_CATEGORIES <- list(
  "#60 Other Refinery Loading Operations" = 60,
  "#86-87 Lightering" = 86:87,
  "#88-90 Ballasting" = 88:90,
  "#91 Vessel Cleaning & Gas Freeing" = 91,
  "#795-798 Tanker and Barge Loading" = 795:798,
  "#799 Tanker Loading, Crude Oil (Non-Refinery)" = 799,
  "#800 Tanker Loading, Gasoline (Non-Refinery)" = 800)
```

### Emissions

#### Introduction {-}

**Category 60** includes all refinery loading operations other than tanker and barge loading. This category accounts for emissions mostly from loading racks and railroad/truck tank car loading.

The following categories include evaporation emissions due to handling of all organic products at marine loading facilities.

**Categories 86 and 87** account for evaporation emissions due to the transfer of cargo (organic materials) from larger ships to smaller ships and barges. Lightering is necessary because large ships are unable to navigate the shallow waters of the San Francisco Bay. Since the mid-2000's, there has been little or no lightering activity in the San Francisco Bay.

**Categories 88-90** account for evaporation emissions due to ballasting crude oil, gasoline, and other materials, respectively. Ballasting is the process of pumping seawater into petroleum holding tanks to make a vessel more stable. When water is pumped into a tank, the contaminated vapor in the tank is displaced into the atmosphere.
Emissions from ballasting are declining because few vessels now calling on Bay Area ports ballast into cargo tanks. Older vessels are being phased out of service in response to the Oil Pollution Act of 1990. Modern vessels have segregated ballast tanks that are used only for ballast water. There are no organic emissions emitted during ballast operations with segregated ballast tanks.

**Category 91** accounts for emissions from gas venting. When a tank vessel unloads its product, organic vapors are left in the compartments. Frequently, vessels vent these vapors to the atmosphere for safety reasons.

**Categories 795-798** account for all evaporative emissions from loading/unloading of gasoline, crude oil and other organic products from marine vessels at the oil refineries. Categories 799-802 account for evaporative emissions from loading/unloading of gasoline and crude oil from all non-refinery operations.

#### Methodologies {-}

##### Area Source Methodologies {-}

For Categories 86 and 87, the refineries within the District were surveyed to obtain the throughputs (in 1000 gallons) transferred for a given year. The monthly variations and county distributions were also obtained from these surveys. Emission factors were obtained from ARB's Emission Inventory Procedural Manual. Since 2005, there has been no lightering activity in the San Francisco Bay.

For Categories 88-90, the amount of material transferred was estimated from data found in the U.S. Army Corps of Engineers' 2008 Waterborne Commerce of the United States, Part 4--Waterways and Harbors-Pacific Coast, Alaska and Hawaii. The emission factors, ballasting amounts for the different fuels, etc. were obtained from California Air Resources Board's Methodology Document on Marine Petroleum Unloading (October 1997).

For Category 91, the following assumptions were made:

1. The average tanker delivering crude oil to the Bay Area has a deadweight tonnage of 120,000 tons. This represents a tanker volume of approximately 32.4 million gallons, assuming a density of 7.4 lbs./gal.
2. In 2008, it was estimated a total of 6,867,568 million gallons of crude was unloaded in Bay Area ports. Assuming the above tanker volume, this represents approximately 212 tanker visits.
3. Purging is not done that often at Bay Area ports. In the report, Oil Tanker Purging & Gas Freeing (December 1999), it was estimated purging occurred in connection with 35 – 50 arrivals per year. In 2004, it was estimated there were 12 venting operations per year. Since 2004, most ship operators perform their venting operations outside the District boundaries.
4. The emission factor used in purging applications is the same one developed for ballasting operations for crude oil (0.9 lb. VOC/1000 gal). Although ballasting and purging are different operations, they involve displacement of vapors remaining in the tank after cargo discharge.

##### Point Source Methodologies {-}

Categories 60 and 795-802 contain point sources permitted by the District. The District updates the data each year on a source-by-source basis using as input:

1. Process material throughputs as reported by the companies.
2. Emissions factors (these may be source specific factors reported by the companies or source test results or general factors, from the AP-42).
3. Emission control factors (device-specific or general).

##### Monthly Variation {-}

For the point source categories (Cats. 60, 795-802), the monthly distribution was estimated based on each company's reported quarterly seasonal throughput data. For the area source categories (Cats. 88-91), the monthly distribution was assumed to be uniform throughout the year.

#### County Distribution {-}

For the point source categories, the county location of each company, as reported in the Data Bank, is used to distribute emissions into each county. For the area source categories, the county distribution was based on the throughputs of products unloaded at the various Bay Area ports, as reported in the U.S. Army Corps of Engineers' 2008 Waterborne Commerce of the United States, Part 4--Waterways and Harbors-Pacific Coast, Alaska and Hawaii.

```{r petprod-marine-load-county-fraction-table}
BY2011_county_fraction_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_county_fractions()
```

### Trends {#petprod-marine-load-trend}

#### History {-}

```{r petprod-marine-load-annual_emissions-ORG-chart, fig.height=6, out.height=600}
BY2011_annual_emission_data %>%
  filter_categories(
    CONSOLIDATED_CATEGORIES) %>%
  filter_pollutants(
    "ORG", "TOG", "ROG") %>%
  chart_BY2011_annual_emissions_by(
    fill = category,
    title = "Organic Emissions") 
```

```{r petprod-marine-load-annual_emissions-PM-chart}
BY2011_annual_emission_data %>%
  filter_categories(
    CONSOLIDATED_CATEGORIES) %>%
  filter_pollutants(
    "PM", "TSP", "PM10", "PM2.5") %>%
  chart_BY2011_annual_emissions_by(
    fill = category,
    title = "Particulate Emissions") 
```

Prior years' growth factors for these categories were based on historical data (i.e. from the U.S. Army Corps of Engineers' Waterborne Commerce reports, the District's databank, etc.) and energy reports.

#### Growth {-}

```{r petprod-marine-load-growth-crosswalk}
BY2011_growth_profile_crosswalk %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_growth_crosswalk()
```

```{r petprod-marine-load-growth-chart, fig.height=20, out.height=2000}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr)
```

The projected growth for the Ballasting categories (Cat. 86-90), the Marine Vessel Cleaning & Gas Venting category (Cat. 91), and the Non-Refinery Tanker/Barge Loading categories (Cat. 799-802) were based on fuels report from the California Energy Commission. Projected growth for all refinery related categories was taken from the California Energy Commission report on California's Petroleum Infrastructure (2011) that predicted California refiners expand distillation capacity to remain relatively flat due to increase in fuel efficiency of vehicles from CAFÉ standards as well as steady transition to alternative fuels in the California market The introduction of reformulated gasoline with lower vapor pressure will help in reducing evaporation emissions.

#### Control {- #petprod-marine-load-control}

```{r petprod-marine-load-lightering-control-chart}
BY2011_annual_control_factor_data %>%
  filter_categories(
    keep(THESE_CATEGORIES, ~ . %in% 86:87)) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant)
```

Categories 86 - 87: [Rule 8-46] (Marine Vessel to Marine Vessel Loading) became effective on July 1, 1991. The overall control efficiency is estimated to be 95%.

```{r petprod-marine-load-ballast_vent-control-chart, fig.height=6, out.height=600}
BY2011_annual_control_factor_data %>%
  filter_categories(
    keep(THESE_CATEGORIES, ~ . %in% 88:91)) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant)
```

Categories 88, 89, and 91: On December 7, 2005, District [Rule 8-44] (Marine Tank Vessel Operations) was amended to extend organic compound control requirements to ballasting (Categories 88 and 89), gas freeing, tank washing, and purging activities (Category 91) from venting tank emissions to the atmosphere. This amendment controls organic emissions from loading operations of gasoline, gasoline blended stock, aviation gas, JP4 jet fuel, crude oil and other liquids with a flash point below 100 ºF. (Since diesel, residual, and distillate fuel oils have flash points above 100 ºF, these fuels from Category 90 were excluded from control requirements. The adoption of this amendment will control organic emissions by 95%.

```{r petprod-marine-load-barge_tanker-control-chart, fig.height=10, out.height=1000}
BY2011_annual_control_factor_data %>%
  filter_categories(
    keep(THESE_CATEGORIES, ~ . %in% 795:802)) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant)
```

Categories 795 - 802: District [Rule 8-44] (Marine Vessel Loading Terminals) became effective July 1, 1991. The overall control efficiency is estimated to be 96%.

***

By: Tan Dinh/Stuart Schultz
Date: January 2014
Base Year: 2011

***

#### Annualized Emission Factors {- #petprod-marine-load-emfac-chart}

```{block type="note"}
Emission factors for category #90 vary by time. (This is not common in the BY2011 inventory.)
```

```{r petprod-marine-load-emfac-chart}
BY2011_annual_area_source_emission_factor_data %>%
  filter_categories(
    keep(THESE_CATEGORIES, ~ . == 90)) %>%
  chart_BY2011_annual_emission_factors_by(
    color = category) 
```

