## Gasoline Truck Transport

```{r petprod-gasoline-truck_transport-setup}
THESE_CATEGORIES <- c(
  "#1600 Cargo Tank" = 1600,
  "#1601 Loading, Return Vapor Hoses" = 1601,
  "#1602 Loading, Main Hoses" = 1602)
```

### Emissions

#### Introduction {-}

Gasoline truck transit losses are similar in many ways to breathing losses associated with petroleum storage. The gasoline is transferred by tank trucks from refineries and bulk plants for delivery to end user outlets. Emissions depend on the vapor tightness of the tank, the pressure relief valve settings, the pressure in the tank at the start of the trip, the vapor pressure of fuel being transported, and the degree of fuel vapor saturation of space in the tank.

#### Methodology {-}

This category accounts for the organic emissions occurring in transit while transporting fuel by tank trucks. Emissions from gasoline cargo tanks include the fugitive emissions and emissions from maintenance. The emission points are from pressure-related fugitive (Cat#1600, Cargo Tank) emissions from the cargo tank fittings and valves, vapor hoses (Cat#1601, Loading-Return Vapor Hoses) after loading into the underground tank, and wetted wall emissions from the product (Cat#1602, Loading-Main Hoses).

- Pressure-related fugitive (Cat#1600, Cargo Tank) emissions are volatile organic vapors leaking from fittings, valves and other connecting points in the vapor collection system on a cargo tank. Pressure inside the cargo tank is caused by solar and reflective heat gains. Due to these heat gains, vapors inside the cargo tank expand and exert pressure to the tank walls, fittings and valves.

- Emissions from the vapor hose (Cat#1601, Loading-Return Vapor Hoses) are a result of vapors trapped inside the hose after product delivery to the underground tank. Some vapors condense inside the hose. When the hose is disconnected from the underground tank and truck fittings, the vapors and condensed vapor inside the hose are emitted into the ambient air.

- Emissions from the product hoses (Cat#1602, Loading-Main Hoses) are a result of residual product clinging to the walls of the hoses. Residual liquid, inside the hose, vaporizes into the ambient air resulting in emissions.

This methodology is presently based on CARB's methodology. TOG emission factors are listed below:

- Pressure-Related (Cat#1600) Losses: 0.588 lbs per 1000 gallons,
- Vapor Hose (Cat#1601) Losses: 0.024 lbs per 1000 gallons,
- Product Hose (Cat#1602) Losses: 0.133 lbs per 1000 gallons.

The estimates of gasoline consumption in the Bay Area were provided by California State Board of Equalization, Fuel Taxes Statistics & Reports and Caltrans Transportation Planning Support Information System (TPSIS). These estimates were made by adjustments of Gasoline Dispensing Facility sales, population, number of registered vehicles, and the number of drivers' license. The throughput for this category is apportioned based upon throughput and TPSIS's estimated gasoline consumption. The total emissions are determined by multiplying the emission factor and the throughput.

#### Monthly Variation {-}

Monthly variation of emissions was based on the monthly California taxable sales data from the Board of Equalization.

#### County Distribution {-}

Emissions distributed into the nine counties were based on Caltrans Transportation Planning Support Information System's breakdown.

### Trends

#### History {-}

```{r petprod-gasoline-truck_transport-annual_emission-chart}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category)
```

Prior to 1999 Base Year, taxable gasoline sales for California obtained from the Board of Equalization were assumed to distribute to all gasoline filling stations.

#### Growth {-}

```{r petprod-gasoline-truck_transport-growth-chart}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr)
```

Gasoline consumption in 2007 reached record levels. However, the gasoline consumption decreased slightly during the economic recession in 2008 - 2010. Projections are based on future gasoline consumption in the Bay Area. Projections are based on future gasoline consumption in the Bay Area.

***

By: Michael Nguyen 
Date: January, 2014 
Base Year 2011

