## Sterilizer Venting {#petprod-sterilizer-vent}

```{r petprod-sterilizer-vent-setup}
THESE_CATEGORIES <- c(
  "#92 Sterilizers (Point)" = 92,
  "#1577 Sterilizers (Area)" = 1577)
```

### Emissions

#### Introduction {-}

Ethylene Oxide is used extensively at large medical facilities in equipment sterilizers as well as in fumigators for the food industry. Ethylene Oxide is widely used due to its ability to kill microbes in difficult to reach places. Category 92 and 1577 account for point and area sources from medical sterilizers in the Bay Area, respectively.

#### Methodology {-}

##### Point Source {-}

Category 92 contains point source emission data reported to the District's permitting department. The District updates the data each year on a source-by-source basis using as input:

1. Process material throughputs as reported by the companies

2. Emissions factors (these may be source specific factors reported by the companies through source test results or applicable general factors, i.e. from the EPA)

3. Emissions control factors (device-specific or general - these may supplied by companies also)

The county, month, and day factors are obtained from the data bank's information on each plant's location, seasonal usage, and days per week of operation.

The point source emissions at present are less than 0.01 tons/day of reactive organics. 

##### Area Source {-}

Category 1577 accounts for non-permitted ethylene oxide emission sources. In 1987, about 206,000 pounds of ethylene oxide was estimated as area source emissions. Because most of these sources are now permitted sources due to [Rule 11-9], the amount of area source emissions is estimated to have dropped to 1050 pounds of sterilizer gas. Emission factor used for ethylene oxide is one. Therefore, all of the ethylene oxide used is emitted as organic emissions.

```{r petprod-sterilizer-vent-county-fraction-table}
BY2011_county_fraction_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_county_fractions()
```

### Trends {#petprod-sterilizer-vent-trend}

#### History {-}

```{r petprod-sterilizer-vent-emission-chart, fig.height=8, out.height=800}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

Actual emissions from the District's permitted sources were used for historical years.

#### Growth {-}

```{r petprod-sterilizer-vent-growth-crosswalk}
BY2011_growth_profile_crosswalk %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_growth_crosswalk()
```

```{r petprod-sterilizer-vent-growth-chart, fig.height=4, out.height=400}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

Growth of ethylene oxide use in sterilizers is estimated to follow population growth. The population data used for growth profiles was obtained from the Association of Bay Area Government's (ABAG's) 2009 "Projections" and the California Statistical Abstracts.

#### Control {-}

```{r petprod-sterilizer-vent-control-chart}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant)
```

Ethylene Oxide is suspected of increasing the risk of stomach cancer and leukemia in humans, because of this risk, the District adopted [Rule 11-9] on November 1, 1989. Note that this Rule is under [Regulation 11], "Hazardous Pollutants".

***

By: Sukarn Claire 
Date: January 2014 
Base Year: 2011
