## Vacuum Truck at Refinery, Marine, Bulk Terminals {#petprod-vacuum-truck}

```{r petprod-vacuum-truck-setup}
THESE_CATEGORIES <- c(
  "#2224 Vacuum Truck" = 2224)
```

### Emissions

#### Introduction {-}

Emissions reported in this category are from the operations of vacuum trucks at refineries, marine, and bulk terminals in the San Francisco Bay Area. A vacuum truck is a transportable, truck-mounted, industrial vacuum system designed to load materials into the truck's containment vessel. Vacuum trucks are capable of loading different types of materials (either pneumatically, by external pump or by gravity feed) into their barrels under a variety of conditions.

#### Methodologies {-}

Emissions are calculated based on throughput and source test data. Throughput data, when available, are obtained from refinery records. Source test data is taken from monitoring measurements during field studies.

Because of the wide variation in test results and because most facilities do not closely track quantities of materials moved by vacuum truck, estimates of emissions and emission reduction for vacuum truck involve significant uncertainty. To determine quantities of materials moved in each category, data was taken for one refinery and scaled for other facilities to arrive at the total.

#### Monthly Variation {-}

Monthly variation for the vacuum truck category was assumed to be uniform throughout the year.

#### County Distribution {-}

With major refinery, marine, and bulk terminal presence, Contra Costa and Solano counties have the largest vacuum truck operations of all the San Francisco Bay Area counties.

```{r petprod-vacuum-truck-county-fraction-table}
BY2011_county_fraction_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_county_fractions()
```

### Trends 

#### History {-}

```{r petprod-vacuum-truck-emission-chart}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category)
```

Vacuum truck historical growth rate was based on data from studies and historical records.

#### Growth {- #petprod-vacuum-truck-growth}

```{r petprod-vacuum-truck-growth-crosswalk}
BY2011_growth_profile_crosswalk %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_growth_crosswalk()
```

```{r petprod-vacuum-truck-growth-chart, fig.height=3, out.height=300}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr)
```

Projected growth for vacuum truck at refineries, bulk, and marine terminals is related to refinery growth. For all refinery related categories, growth was taken from the California Energy Commission report on California's Petroleum Infrastructure (2007) that predicted California refiners expand distillation capacity to increase at a rate of approximately one percent per year.

#### Control {-}

```{r petprod-vacuum-truck-control-chart, fig.height=3, out.height=300}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant,
    flag_years = CY(2011, 2030))
```

Vacuum truck is regulated under District's [Rule 8-53] which established an emission limit that applies at the vapor exhaust outlet of the vacuum truck or associated equipment. The rule also establishes a limit for vapor leads and for liquid leaks from vacuum truck equipment.

***

By: Tan Dinh
Date: January 2014
Base Year: 2011
