## Miscellaneous Organic Evaporation

```{r petprod-evap-other-setup}
THESE_CATEGORIES <- c(
  "#282 Other Organic Compounds Evaporation" = 282)
```

### Emissions

#### Introduction {-}

This category contains various types of equipment identified in the permit data bank as not defined in the many other categories and therefore designated as "other" equipment. Emissions from this category are from various sources and different industrial processes. The emissions for these point sources are contained in the permit data bank.

#### Methodology {-}

This category contains emissions from point sources only. Point source emissions are calculated from a facility’s equipment operating data submitted as part of the permit approval process. The Data Bank contains throughput information from sources submitted by individual plants. Emissions are then calculated by using specific emission factors for a particular source operation supplied by the company. If no specific factor is available, a generalized factor developed by district staff engineer is used to determine emissions.

#### Monthly Variation {-}

The data bank contains throughput data for each month provided by companies holding District permits.

#### County Distribution {-}

Emissions distributed into counties were based on actual locations of the plants in the Bay Area.

### Trends

#### History {-}

```{r petprod-evap-other-emission-chart, fig.height=6, out.height=600}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category)
```

```{r petprod-evap-other-BY-vs-DB-chart, fig.height=10, out.height=1000}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY_vs_DB_point_source_annual_emissions()
```

The historical growth profile was based on a combination of prior emissions data and the California Air Resources Board Manufacturing Employment growth profile.

#### Growth {-}

```{r petprod-evap-other-growth-chart, fig.height=3, out.height=300}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr)
```

Future projections of emissions to 2030 are based on the Association of Bay Area Government’s (ABAG’s) 2009 Manufacturing Employment growth profile.

#### Control {-}

```{r petprod-evap-other-control-chart, fig.height=3, out.height=300}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant)
```

Sources in this category may be subject to [Regulation 8-4] (General Solvent & Surface Coating Operations). The purpose of this Rule is to “limit emissions of volatile organic compounds from the use of solvents and surface coatings in any operation other than those specified by other Rules of the Regulation 8.” Originally passed in 1980, this rule has been amended several times—the latest being in 2002 regarding surface preparation standards.

***

By: Stuart Schultz 
Date: January 2014 
Base Year 2011
