## Natural Gas Distribution

```{r petprod-NG_distrib-setup}
THESE_CATEGORIES <- c(
  "#61 Power Plant Fuel Use" = 61,
  "#868 Other Fuel Use" = 868)
```

### Emissions

#### Introduction

Emissions associated with the transmission of natural gas are mostly fugitive organic emissions that occur due to the leaks in pipeline. Components such as valves, flanges, pumps, compressors, and pressure relief valves (PRVs) are the potential leak sources.

Categories 61 and 868, account for fugitive organic emissions including methane (CH4) from natural gas distribution system in the San Francisco Bay Area. Emissions from Pacific Gas and Electric's (PG&E's) pipeline system that distributes natural gas for its own use are covered in Category #61. Emissions from PG&E's pipeline system that distributes natural gas to residential, commercial and industrial customers are covered in Category #868.

#### Methodology

Fugitive emissions occur from leaks in the pipeline distribution system. Prior to 1990, an emission factor of 0.7% by volume of gas distributed was used. This factor was based on the South Coast Air Quality Management District report "Estimated Fugitive Emissions from Natural Gas Transmission for Calendar Year 1979", July, 1980. Since 1990, an emission factor of 0.2% has been used for both distribution systems: PG&E's own usage (Category #61) and PG&E's customers (Category #868). This emission factor is based on the 1990 PG&E report titled “Unaccounted-For Gas Project”. Emission Factors in pounds per thousand cubic feet of gas (lb/MCF) are shown below.

|  Categories  | Total Organics (TOG) | Methane (CH4) |
|:------------:|:--------------------:|:-------------:|
|  `61`, `868` |         88.0         |      85.4     |

#### County Distribution

County distributions for Category #61 and #868 are based on natural gas usage data obtained from the California Energy Commission (CEC), PG&E, and City of Palo Alto.

#### Temporal Variation

The daily, weekly and monthly emission rates are considered to be uniform.

### Trends

#### History

```{r petprod-NG_distrib-annual_emissions-chart, fig.height=6, out.height=600}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

In general, emissions increase as activity increases and emissions decrease as activity decreases. In recent years, emissions for category #868 have been increasing, while emissions for category #61 have been on the decrease due to PG&E’s divestments in power plants.

For Base Year 1983, all natural gas distribution losses were handled as a single category which had been designated as Category #43. The category has been subsequently split into two categories (#61 and #868) since Base Year 1987.

For Category #61 up to base year 2008, it was assumed that annual emissions would tend to follow two components: services industry employment and population by county in the District. As such, a hybrid growth profile was developed based on 50% of the appropriate county services industry employment value and 50% of the appropriate county population value in combination with CEC’s natural gas data. For Category #868 up to base year 2008, it was assumed that annual emissions would tend to follow: manufacturing industry employment and population by county in the District in combination with CEC’s natural gas consumption forecasts. As such, a hybrid growth profile was developed based on 50% of the appropriate county manufacturing industry employment value and 50% of the appropriate county population value in combination with CEC’s natural gas data. For previous forecasts, the employment and population data was obtained from the Association of Bay Area Government's (ABAG’s) 2009 "Projections" reports.

#### Growth

```{r petprod-NG_distrib-annual_growth-chart, fig.height=6, out.height=600}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

Annual demand for natural gas varies in response to business conditions and annual temperatures but has been generally declining or flat over recent years. This is due in part to historically low number of heating degree days and building and appliance efficiency standards, utility and public agency programs, and price and other effects. This trend is projected to continue with a population growth at a faster rate than total demand for natural gas.

By: S. Claire
Date: January 2014 
Base Year: 2011
