## Storage Tanks {#petprod-petref-storage}

```{r petprod-petref-storage-setup}
THESE_CATEGORIES <- c(
  "#55 Cone Roof" = 55,
  "#56 External Floating Roof" = 56,
  "#57 Internal Floating Roof" = 57,
  "#58 Other Types" = 58,
  "#84 Cone Roof" = 84,
  "#85 Other Types" = 85,
  "#940 Tank Cleaning" = 940,
  "#1902 Cone Roof (Area)" = 1902,
  "#1903 Other Types (Area)" = 1903)
```

### Emissions

#### Introduction {-}

Tanks are used at petroleum refineries to store raw materials, intermediate products, finished products, and wastes. There are numerous intermediate products in a refinery including liquefied petroleum gas, gasoline, kerosene, diesels, and fuel oils. The waste products include wastewater, spent acids, and oily sludge.

Categories 55-58 contain point source emissions from refineries tanks, and categories 84- 85 account for point souce emissions from tanks at other sites. Category 940 accounts for point source emissions from cleaning of all storage tanks. Category 1902 and 1903 accounts for area source emissions from storage tanks.

Storage tanks at bulk plants and gasoline stations are inventoried in sections 6.4 and 6.9, respectively.

#### Methodologies {-}

The categories for storage tanks contain emissions from both point and area sources. Tank emissions are calculated using equations and emission factors from U.S. EPA’s Compilation of Air Pollutant Emisssion Factors, AP-42, Volume I: Station Point and Area Sources. The primary criteria pollutant emitted from storage tanks include hydrocarbon vapors or volatile organic compounds (VOCs).

The predominant types of storage tanks found in a refinery include: 

- Fix roof tanks
- External floating roof tanks
- Internal floating roof tanks
- Conservation tanks, pressure tanks, and others

The types of tank along with the following parameters (given below) are used to calculate emissions.

- Tank diameter
- Paint factor
- Tank height
- Vapor space
- Temperature change
- Tank volume
- Throughput
- Stored material
- Factors specific to stored material

Point source emissions are obtained from the District’s data bank system. The data bank
contains information submitted by the individual refinery by tank sources. Area Source emissions are derived based on an estimated ratio between area and point source throughputs via tank type.

#### Monthly Variation and County Distribution {-}

The county, month, and day factors are obtained from the data bank's information for each category.

### Trends

#### History {-}

```{r petprod-petref-storage-annual_emissions-chart, fig.height=6, out.height=600}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```
Historical emissions have varied with refinery throughputs.

#### Growth {-}

Projected growth for all refinery related categories was taken from the California Energy Commission report on California’s Petroleum Infrastructure (2011) that predicted California refiners expand distillation capacity to remain relatively flat. This is due to increase in fuel efficiency of vehicles from CAFÉ standards as well as steady transition to alternative fuels in the California market. California refiners have recently added and will continue to add more process units to produce reformulated gasoline. However, no large increases in emissions are expected.

#### Control {-}

```{r petprod-petref-storage-annual_control-chart, fig.height=12, out.height=1200}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant)
```

[Regulation 8-5] controls emissions from the storage of organic liquids. Control efficiencies are estimated to range from 17% to 96%, depending on the type of tank, percentage of sources with true vapor pressures above 0.5 psi, and average true vapor pressure of the corresponding category. The following table show the control and rule efficiencies. (Sources with true vapor pressure greater than 0.5 psi are affected by this rule.)

**FIXME: INSERT TABLE**

***

By: Tan Dinh
Date: January 2014 
Base Year: 2011
