## Animal Waste, Livestock {#misc-animal-livestock}

```{r misc-animal-livestock-setup}
THESE_CATEGORIES <- c(
  "#1619 Dairy Cattle" = 1619,
  "#1620 Range Cattle" = 1620,
  "#1621 Broilers" = 1621,
  "#1622 Layers" = 1622,
  "#1623 Turkeys" = 1623,
  "#1624 Swine" = 1624,
  "#1625 Sheep" = 1625,
  "#1626 Horses" = 1626,
  "#1627 Other Livestock" = 1627)
```

### Emissions

#### Introduction {-}

Livestock emissions including dairy cattle, range cattle, poultry, swine, sheep, horses, and goats are assumed to be directly related to animal population. Most available population data is based on annual sales data. For dairy cattle, range cattle, and feedlot cattle, year 2000 population was derived from the California Department of Food and Agriculture's (CDFA) summary of cattle and calves inventory of January 1, 2001. The populations are developed by the United States Department of Agriculture, and the CDFA 2001 Agricultural Resources Directory.

#### Methodology {#misc-animal-livestock-methodology -}

This methodology is presently based on ARB's methodology. Livestock population in the Bay Area was divided into subcategories: dairy cattle, range cattle, poultry (layers and broilers), swine, sheep, horses, and goats. Table \@ref(tab:misc-animal-waste-livestock-throughputs-table) shows livestock population in the Bay Area.

```{r misc-animal-waste-livestock-throughputs-table}
#' 
#' 1. Pull throughputs
#' 2. Convert county abbrs to names
#' 3. Complete data for SF (all zeros)
#'
kable_data <-
  BY2011_area_source_throughput_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  filter_years(
    CY(2011)) %>%
  mutate(
    cnty_id = encode(cnty_abbr, DST_COUNTY_CODES),
    county = decode(cnty_id, DST_COUNTY_NAMES)) %>%
  select(
    category,
    county,
    tput_qty) %>%
  mutate_at(
    vars(county),
    ~ factor(., levels = names(DST_COUNTY_NAMES))) %>%
  tidyr::complete(
    category,
    county,
    fill = list(
      tput_qty = 0))

#' 
#' 1. Spread by category
#' 2. Add row for totals
#' 3. Format as counts (with commas)
#'
kable_content <-
  kable_data %>%
  spread(
    category,
    tput_qty,
    fill = 0) %>%
  janitor::adorn_totals(
    "row", fill = "") %>%
  mutate_at(
    vars(-county),
    ~ formattable::accounting(., digits = 0)) 

kable_content %>%
  kable(
    caption = "Livestock populations in the Bay Area.") %>%
  kable_styling(
    full_width = FALSE,
    bootstrap_options = c(
      #"striped", 
      "condensed")) %>%
  kableExtra::row_spec(
    nrow(kable_content),
    bold = TRUE)
```

For each category, the emissions are calculated by multiplying emission factor and population of each animal type.

#### Monthly Variation {-}

Monthly distribution was estimated evenly over the twelve months.

#### County Distribution {-}

The county distribution was based on the cattle population in Table \@ref(tab:misc-animal-waste-livestock-throughputs-table) for the nine counties.

```{r misc-animal-livestock-county-fraction-table}
BY2011_county_fraction_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_county_fractions()
```


#### History {-}

```{r misc-animal-livestock-emission-chart, fig.height=12, out.height=1200}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

Emissions through the years were estimated based on the ARB's growth profile on dollar values of Agricultural stock for each county.

#### Growth {-}

```{r misc-animal-livestock-growth-crosswalk}
BY2011_growth_profile_crosswalk %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_growth_crosswalk()
```

```{r misc-animal-livestock-growth-chart, fig.height=12, out.height=1200}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

The growth rate varies by county and by livestock and there is currently not a general surrogate to indicate the livestock growth or decline. In most cases, zero growth is assumed for livestock emissions, which is probably reasonable for most areas in the state. Projections to year 2030 are based on the ARB's growth profile.

***

By: Michael Nguyen 
Date: February, 2014 
Base Year 2011
