## Accidental Automobile Fires {#misc-fire-auto}

```{r misc-fire-auto-setup}
THESE_CATEGORIES <- c(
  "#753 Accidental Automobile Fires" = 753)
```

### Emissions

#### Introduction {-}

Category 753 is an area source category that estimates criteria pollutant (particulate, organic, NO~x~, SO~x~, and CO) and greenhouse gas emissions (CO~2~, CH~4~, and N~2~O) from accidental automobile fires. The method used to calculate emissions for this category conforms to the method used by the California Air Resources Board (CARB).

#### Methodology {- #misc-fire-auto-methodology}

The total number of automobile accidental fires in California was acquired from the state fire marshal's office. Automobile fires were apportioned to the Bay Area based on Bay Area population as compared to California's total population.

The emission factors for automobile fires were derived from the Environmental Protection Agency's (EPA's) document AP-42, Section 2.2.2 and 2.4.2. Table 2.2-1 of AP-42 lists the emission factors for uncontrolled auto body incineration, which are based on automobiles that have been partially stripped (tires, seats, etc. removed). Table 2.4-1 lists the emission factors for open burning of automobile upholstery, belts, hoses, and tires in common.

It is assumed that tires are burned in 60% of the automobile fires. Composite emission factors were calculated as a weighted average of the emission factors listed in Table 2.2-1 and 2.4-1 of AP-42, with the assumption that the average car body weighs 3,700 pounds and the components weigh 500 pounds. The criteria pollutant composite emission factors (Lb/Fire) are listed below:

```{r misc-fire-auto-emission-factors-PONSCO-table}
BY2011_annual_area_source_emission_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_emission_factors(
    pollutants = c(
      "PM", "TOG", "NOx", "SO2", "CO"),
    caption = "Composite emission factors (lb/fire).")
```

The emission factors for greenhouse gas inventory were developed using above information and emission coefficient data from the Environmental Protection Agency (EPA), the U.S. Department of Energy's (DOE's) Energy Information Administration (EIA) and The California Energy Commission (CEC). The Greenhouse gas composite emission factors (Lb/Fire) are as follow:

```{r misc-fire-auto-emission-factors-GHG-table}
BY2011_annual_area_source_emission_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_emission_factors(
    pollutants = c(
      "CO2", "CH4", "N2O"),
    caption = "Composite emission factors for GHGs (lb/fire).")
```

#### Temporal Variation {-}

The monthly activity and the weekly activity are uniform. The daily activity occurs primarily during daylight hours.

#### County Distribution {-}

Automobile fires were apportioned to the Bay Area counties based on population by county. This was used directly in the county distribution except for Solano and Sonoma which were adjusted to include only areas inside the District using household population.

```{r misc-fire-auto-county-fraction-table}
BY2011_county_fraction_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_county_fractions()
```

### Trends

#### History {-}

```{r misc-fire-auto-emission-chart, fig.height=12, out.height=1200}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

Historical trends were developed using data from the State Fire Marshal's Office and growth in Bay Area population.

#### Growth {-}

```{r misc-fire-auto-growth-crosswalk}
BY2011_growth_profile_crosswalk %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_growth_crosswalk()
```

```{r misc-fire-auto-growth-chart, fig.height=4, out.height=400}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

Emission projections for this category are based on population growth in the San Francisco Bay Area. Population data used for emission growth profile was obtained from the Association of Bay Area Government's (ABAG's) 2009 "Projections" reports.

***

By: Sukarn Claire 
Date: January 2014 
Base Year: 2011
