## Accidental Vegetation Fires {#misc-fire-veg}

```{r misc-fire-veg-setup}
THESE_CATEGORIES <- c(
  "#1580 Accidental Vegetation Fires" = 1580)
```

### Emissions

#### Introduction {-}

Category 1580 is an area source category that accounts for criteria pollutant (particulate, organic, NO~x~, SO~x~, and CO) and greenhouse gas emissions (Biogenic-CO~2~, CH~4~, and N~2~O) from wildfires in woodland, timber, brush and grass.
Carbon Dioxide emissions from this category are considered to be biogenic emissions. Biogenic Carbon Dioxide (Bio-CO~2~) emissions are a subset of total CO~2~ emissions which are emitted from materials that are derived from living cells, excluding fossil fuels, limestone and other materials that have been transformed by geological processes. Bio- CO~2~ originates from carbon that is present in materials such as wood, paper, vegetable oils and food, animal, and yard waste.

Planned or prescribed fires such as weed burning, field crops, prunings, range improvement burning and forest management are covered in categories 315-319.

#### Methodology {-}

Methodology for this category is in accordance with the California Air Resources Board’s (CARB’s) document "Methods for Assessing Area Source Emissions in California" for the Wildfires. Activity data (acreage burnt) estimates were obtained from the California Department of Forestry and Fire Protection (CDF) and CARB.
Wildfire emissions are calculated using the Geographic Information System (GIS) based Emission Estimating System (EES) model developed for ARB by UC Berkeley’s Center for the Assessment and Monitoring of Forest and Environmental Resources (CAMFER) laboratory. Wildfire footprint is overlaid on vegetation landcover map, calculating the amount of each fuel consumed in the fire. Fuel loading is assigned for each fuel component that makes up the vegetation type.

Emission factors and vegetation acreage consumed vary from fire season to fire season depending on type of vegetation consumed and weather conditions. For example, average composite emission factors and amounts of acreage burnt in the Bay Area by county are shown below for year <span class="strike">2008</span> 2011.

```{r misc-fire-veg-emfac-table}
BY2011_annual_area_source_emission_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_emission_factors(
    pollutants = union(
      BY2011_POLLUTANTS,
      c("CO2_bio", "CH4", "N2O")),
    caption = "Composite emission factors (lb/acre).")
```

```{r misc-fire-veg-throughputs-table}
kable_data <-
  BY2011_area_source_throughput_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  filter_years(
    CY(2011)) %>% # FIXME: update for BY2015
  mutate(
    cnty_id = codec::encode(cnty_abbr, DST_COUNTY_CODES),
    county = codec::decode(cnty_id, DST_COUNTY_NAMES)) %>%
  tabulate_throughputs_by(
    county,
    digits = 0) %>%
  drop_vars(
    tput_unit) %>%
  mutate_at(
    vars(everything()),
    ~ formattable::accounting(., digits = 0))

kable_data %>%
  kable_BY2011(
    totals = "column",
    caption = "Acreage burned.")
```

Other sources for the vegetation combustion emissions related information are the U.S. Department of Energy’s (DOE’s) Energy Information Administration (EIA); the Environmental Protection Agency’s (EPA’s) document AP-42, and the California Energy Commission (CEC).

#### County Distribution {-}

County distribution of emissions is based on acreage burnt in each of the San Francisco Bay Area counties.

#### Monthly Variation {-}

On the basis of historical data, the California Department of Forestry and Fire Protection (CDF) suggests most of the wild fires occurring from mid-May to mid-November. The percentage of wild fires by month is estimated as follow: May - 5%, June - 10%, July - 15%, August - 20%, September - 25%, October - 20% and November - 5%.

### Trends

#### History {-}

```{r misc-fire-veg-emission-chart, fig.height=12, out.height=1200}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

Prior to Base Year 2002 wildfire category 1580 was split into two categories, category 751 (Timber and Brush) and category 752 (Grass and Woodland).

#### Growth {-}

```{r misc-fire-veg-growth-chart, fig.height=4, out.height=400}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

Actual acreage burned can vary widely from year to year depending on weather conditions. Therefore, greater number of wildfires may occurr during a relatively dry year. Future emission trends are based on the average number of acres burned over the previous ten-year period in the San Francisco Bay Area.

***

By: Sukarn Claire 
Date: January 2014 
Base Year: 2011
