## Coatings & Inks {#chem-fac-coatings}

```{r chem-fac-coatings-setup}
THESE_CATEGORIES <- c(
  "#23 Coatings and Inks Manufacturing" = 23)
```

### Emissions

#### Introduction {-}

Organic emissions from the manufacturing of coatings and inks are reported in this category. Coatings processes includes mixes, blends, or compounding of paints, varnishes, lacquers, enamels, shellac, or sealers from raw materials. Ink manufacturing involves mixes, blends or compounding other raw materials to produce the ink. Printing inks consist of pigments, which produce the desired colors, binders which lock the pigment to the substrate, and solvents, usually organic compounds that dissolve the pigments and binders. A majority of the emissions originate from mixing and cleaning operations. Throughput information of each source is reported by the facilities and is stored in the District's Data Bank system.

#### Methodology {-}

Organic emissions are calculated by using data on the reported throughput, the specific materials ( i.e. density, percent VOC in coatings, etc.) as supplied by the companies through the District "S" and "G" forms. The District updates the data each year on a source-by-source basis using as input:

1. Process material throughputs as reported annually by the chemical manufacturing companies.

2. Emissions factors (these may be source specific factors reported by the companies through source test results or applicable general factors, i.e. from the EPA).

3. Emissions control factors (device-specific or general - these may be supplied by the companies also).

The county, month, and day factors are obtained from the data bank's information on each plant's location, seasonal usage, and days per week of operation.

#### Monthly Variation {-}

Monthly distribution was estimated based on major coatings and inks manufacturer's reported quarterly percent throughput. An attempt was made to weight-average into monthly factor, with March through August being the high season and November and December being the lowest.

#### County Distribution {-}

The county location of each company as reported in the Data Bank is used to distribute emissions into each county.

### Trends

#### History {-}

Emissions have been generally increasing due to increasing demand on coatings and inks, which has been about 4 to 8 percent per year in the 1980's. District [Regulation 8, Rule 35](https://www.baaqmd.gov/rules-and-compliance/rules/reg-8-rule-35-coating-ink-and-adhesive-manufacturing), pertaining to emissions control from mixing operations at coating and ink facilities was adopted in May 1984. Since the adoption of the regulation, there have been significant changes in the manufacturing process. It was estimated there was a 55% emission reduction due to the implementation of the regulation.

```{r chem-fac-coatings-emission-chart, fig.height=8, out.height=800}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category)
```

#### Growth {-}

```{r chem-fac-coatings-growth-chart}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr)
```

Projections to year 2030 was based on growth profile of ARB's Manufacturing in the Printing Industry, and is expected to grow at a only 1-2 percent per year.

#### Control {- #chem-fac-coatings-control}

```{r chem-fac-coatings-control-chart}
BY2011_annual_control_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_control_factors_by(
    color = pollutant)
```

[Regulation 8, Rule 35](https://www.baaqmd.gov/rules-and-compliance/rules/reg-8-rule-35-coating-ink-and-adhesive-manufacturing) was amended effective January 1993, eliminating the exemptions from small users, requiring lids on all portable and stationary mixing vats, and other cleaning provisions. Control effectiveness of the amended regulation has resulted in an 84% emission reduction since 1993.

***

By: Tan Dinh
Date: January 2014
Base Year: 2011
