## Locomotives

```{r mobile-locomotive-setup}
THESE_CATEGORIES <- c(
  "#936 Locomotive Operations, Road Hauling" = 936,
  "#1681 Locomotive Operations, Switching" = 1681,
  "#1722 Locomotive Operations, Passenger" = 1722)
```

### Emissions

#### Introduction {-}

Locomotives are an important mode of transportation for the movement of goods in the state of California. The ability of locomotives to haul a large amount of goods and the established network of rails throughout the state of California make locomotive an ideal transportation mechanism for goods movement. This emission inventory report accounts for emissions from three major types of locomotive operations. They include road hauling locomotive operations (category 936), switching locomotive operations (category 1681), and passenger operations (category 1722).

#### Methodology {-}

Locomotive emission estimates for the San Francisco Bay Area are obtained from the California Air Resources Board (CARB). CARB locomotive emission inventory uses Booz-Allen Hamilton’s, “Locomotive Emission Study”, published in 1992 as a guideline for emission estimates. This study was commissioned by the Locomotive Emission Advisory Committee under Assembly Bill 234 that authorized CARB to conduct, jointly with the California railroad industry, a study of railroad locomotive emissions. An inventory was developed from this report and became the baseline inventory.

Since 1992, CARB has made updates to the locomotive emission inventory. In 2003, CARB updated the emission inventory by revising growth assumptions. In 2005, CARB updated the inventory to incorporate fuel correction factors, add passenger train data, and Class III locomotives. These changes have made a significant impact on the total inventory.
Greenhouse gas emissions for locomotives are calculated by multiplying activity data by standardized emission factors for each greenhouse gas. These emission factors take into account fuel-specific carbon content and the percent of carbon that oxidizes to convert to greenhouse gas emissions. Emission factor data was obtained from the U.S. Department of Energy’s (DOE’s), Energy Information Administration (EIA).

### Trends {-}

Historical and future emissions (1970-2010) were estimated based upon the CARB emission data.

#### Growth {-}

```{r mobile-locomotive-annual_emissions-chart, fig.height=12, out.height=1200}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

Growth factors for locomotives are based on U.S. industrial production and various railroad statistics available from the Association of American railroads. It is assumed that railroad activity would increase primarily in the area of goods movement since greater goods are needed to accommodate for an increasing population.

#### Control {-}

```{r mobile-locomotive-annual_growth-chart, fig.height=6, out.height=600}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

In 1997, the U.S. EPA finalized the locomotive emission standard regulation. Additionally, projected emissions include expected benefits from ARB's Clean Diesel Regulations (beginning 1993). In 2005, CARB entered into an agreement with Union Pacific Railroad and BNSF to reduce emissions from locomotives throughout California. The agreement establishes a statewide program to reduce diesel particulate emissions from locomotives at the State’s rail yards by phasing out non-essential locomotive idling, installing idling reduction devices, and maximizing the use of low sulfur fuel. It is expected that the elements of these agreement will produce approximately 20% reduction in diesel particulate matter emissions around the rail yards.

***

By: Tan Dinh
Date: December 2010
Base Year: 2011
