## Commercial Aircraft, Piston

```{r mobile-air-com-piston-setup}
THESE_CATEGORIES <- c(
  "#1130 Commuter/Taxi Aircraft (SFO)" = 1130,
  "#1131 Commuter/Taxi Aircraft (OAK)" = 1131,
  "#1132 Commuter/Taxi Aircraft (SJC)" = 1132)
```

### Emissions

#### Introduction {-}

Considered in these categories are criteria pollutant (particulate, organic, NO~x~, SO~x~, and CO) and greenhouse gas emissions (CO~2~, CH~4~, and N~2~O) from commercial piston aircrafts during their operations at the three major airports in the Bay Area, namely, San Francisco International (SFO), Oakland International (OAK), and San Jose International (SJC). A classification system for commercial aircraft was formulated consisting of major passenger, cargo, and commuter/air taxi. The commuter/taxi class is primarily of the piston type.

In the piston engine, the basic element is the combustion chamber. Mixtures of fuel and air are burned in this chamber from which energy is extracted by a piston and crank mechanism driving a propeller. The turboprop engine has a propeller turned through a system of gears from a gas turbine system; it usually delivers more thrust--up to medium- high subsonic airspeeds. The majority of the commuter/taxi aircraft use this turboprop engine propulsion.

#### Methodology {-}

The pollutants emitted by an aircraft during take-off and landing operations are dependent on the emission rates and the duration of these operations. The emission rates are dependent upon the type of engine and its size or power rating. An aircraft operational cycle includes landing and takeoff (LTO) cycle. For criteria pollutant emission inventory, an LTO cycle includes all normal operational modes performed by an aircraft between its descent from an altitude of about 2,300 feet on landing, and subsequent takeoff to reach the 2,300-foot altitude. The 2,300-foot limit is a reasonable approximation to the meteorological mixing depth over the Bay Area metropolitan areas. The term “operation” is used by the Federal Aviation Administration (FAA) to describe either a landing or a take-off cycle. Therefore, two operations make one LTO cycle.

For criteria pollutant emission calculations, the aircraft LTO cycle is divided into five segments or operational “modes” and categorized by:

1. Landing approach (descent from about 2,300 ft. to touch down), 2. Taxi/idle-in,
3. Taxi/idle-out,
4. Take-off,
5. Climb out (ascent from lift-off to about 2,300 ft.).

The emissions are based on the time of operation in each mode and the emission rates of the engines. The time in the landing approach and climb out modes are assumed to be 3.02 minutes and 1.55 minutes, respectively. Take-off time of 0.95 minute (including 0.25 minute for reverse thrust) is fairly standard for commercial aircraft and represents the time for initial climb from ground level to about 500 feet. The time in taxi/idle mode usually varies with airports.

For greenhouse gas (GHG) emission inventory, in addition to LTO cycle explained above, the aircraft landing approach and climb out modes above 2,300 feet elevation and aircraft cruise mode in the District's air space is also included.

The information on number of aircraft operations and fleet mix was obtained from the three major commercial airports in the Bay Area, the Federal Aviation Administration (FAA), and the Metropolitan Traffic Commission (MTC). Emission rates vary according to engine type and operating mode. Modal emission rates for aircraft engines in general commercial use were obtained from the FAA's Aircraft Engine Emission Database, the U.S. Environmental Protection Agency (EPA), International Civil Aviation Organization (ICAO), and Intergovernmental Panel on Climate Change (IPCC).

$$
\text{EMF} = \text{N} \times \sum{\left( v_e / v_t \right)_{m,p}} \times \text{TIM}
$$
where:

<div class="nobullet">

- $\text{EMF}$ = emission factor (lb/LTO);
- $\text{N}$ = number of engines;
- $\left( v_e / v_t \right)_{m,p}$ = engine emission rates (lb/hr) at mode $m$, pollutant $p$; and
- $\text{TIM}$ = time in mode $m$ (hr).

</div> 

##### Sample calculations {-}

TOG emissions for ATR72 (Commuter/Taxi aircraft):

$$
10,961\ \text{LTO/yr} \times 5.07\ \text{lb/LTO} \div 365\ \text{day/yr} \div \text{2000 lb/ton} = 0.076\ \text{ton/day}\ \text{TOG}
$$

#### County Distribution {-}

The county location of each airport was used to distribute emissions into each county, where SFO is in San Mateo County; OAK is in Alameda County, and SJC in Santa Clara County.

```{r mobile-air-com-piston-county-fraction-table}
BY2011_county_fraction_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_county_fractions()
```

#### Monthly Variation {-}

Monthly distribution was based on the average monthly number of operations at each airport.

### Trends 

#### History {-}

```{r mobile-air-com-piston-emission-chart, fig.height=14, out.height=1400}
BY2011_annual_emission_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_emissions_by(
    fill = category) 
```

Emissions through the years were estimated based on the above methodology and the actual number of operations from each airport. Selected years were calculated with corresponding estimates of the aircraft fleet mix during those times.

#### Growth {-}

```{r mobile-air-com-piston-growth-crosswalk}
BY2011_growth_profile_crosswalk %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  kable_BY2011_growth_crosswalk()
```

```{r mobile-air-com-piston-growth-chart, fig.height=6, out.height=600}
BY2011_annual_growth_factor_data %>%
  filter_categories(
    THESE_CATEGORIES) %>%
  chart_BY2011_annual_growth_factors_by(
    color = cnty_abbr) 
```

The continuing effort in aircraft improvement, development of newer engine technology and their phasing in will result in reduced emissions. Airport noise regulations have forced changes to the commercial aircraft fleet resulting in replacement of loud and dirtier engines with newer, quieter, and cleaner burning engines. There is a continuing trend in the use of larger aircraft thereby increasing the passenger to LTO ratio. This will reduce the number of LTOs and consequently, lower emissions.

The projections for number of operations and fleet mix at each airport were developed based on combination of information from the airports, the FAA, and the MTC's Regional Airport System Plans (RASP). Emissions for selected years were calculated based on above methodology. Emission values for other years were obtained by interpolation and extrapolation method.

***

By: Sukarn Claire 
Date: January 2014 
Base Year: 2011
